---
title: "Correlation among Parameter Estimates: Level-1 Factor Covariance"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r init, warning=FALSE, message=FALSE}
rm(list=ls())
source(paste0(getwd(),"/code/load_packages.R"))
source(paste0(getwd(),"/code/get_data.R"))

# subset to data with admissible replications
sim_results <- filter(sim_results, Converge==1 & Admissible==1)

```

```{r}
sessionInfo()
```

# General Descrition

On this page, we are investigating the correlation among parameter estimates between estimation methods.
We do this by

1. Subsetting the data to the parameter of interest
2. Reshaping the data to wide
3. Compute the correlation
4. Compute the proportion of admissible cases by comparison (i.e., proportion of replications that were used to compute correlation). This gives us an indication of how convergence varied across estimation methods
5. Reshape to long data for plotting
6. Plot correlation estimates in boxplots with points overlayed

# Factor Covariance: Level-1

## Data Manipulation

```{r}

# keep variables
keepVar <- c("Condition", "Replication", "ss_l1", "ss_l2", "icc_ov", "icc_lv", "Estimator", "psiW12")

sim_res1 <- sim_results[, keepVar]

sim_res1 <- sim_res1%>%
  pivot_wider(id_cols=c("Condition","Replication", "ss_l1", "ss_l2", "icc_ov", "icc_lv"),
              names_from = "Estimator",
              values_from = "psiW12")

cor.est <- sim_res1 %>%
  group_by(ss_l1, ss_l2, icc_ov, icc_lv) %>%
  summarise(
    r_mlr_ulsmv = cor(MLR, ULSMV,use = "pairwise.complete"),
    cprop_mlr_ulsmv = (1-(sum(is.na(MLR + ULSMV))/500)) ,
    r_mlr_wlsmv = cor(MLR, WLSMV,use = "pairwise.complete"),
    cprop_mlr_wlsmv = (1-(sum(is.na(MLR + WLSMV))/500)),
    r_ulsmv_wlsmv = cor(ULSMV, WLSMV,use = "pairwise.complete"),
    cprop_ulsmv_wlsmv = (1-(sum(is.na(ULSMV + WLSMV))/500))
  )

a1 <- cor.est %>%
  pivot_longer(cols= starts_with("r_"),
               names_to= "Cor",
               values_to = "Est") %>%
  mutate(Cor = substring(Cor, 3))

a2 <- cor.est %>%
  pivot_longer(cols= starts_with("cprop_"),
               names_to= "Cor",
               values_to = "Cprop")%>%
  mutate(Cor = substring(Cor, 7))

cor.est <- left_join(a1[,c(1:4,8:9)], a2[,c(1:4,8:9)])

cor.est$Cor <- factor(cor.est$Cor,
                      levels=c("mlr_ulsmv", "mlr_wlsmv", "ulsmv_wlsmv"),
                      labels=c("cor(MLR, ULSMV)",
                               "cor(MLR, WLSMV)",
                               "cor(ULSMV, WLSMV)"),
                      ordered=T)

cor.est$C90 <- as.factor(ifelse(cor.est$Cprop >= 0.9, ">= 90%", "< 90%"))
cor.est$C95 <- as.factor(ifelse(cor.est$Cprop >= 0.95, ">= 95%", "< 95%"))

```

## Plots Between Conditions

```{r}

cols=c("< 90%"="#56B4E9", ">= 90%"="#CC79A7")
p <- ggplot(cor.est, aes(x=Cor, y=Est)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(data=filter(cor.est, C90=="< 90%"),
              width=0.3, aes(x=Cor, y=Est, color="< 90%")) +
  geom_jitter(data=filter(cor.est, C90==">= 90%"),
              width=0.3, aes(x=Cor, y=Est, color=">= 90%")) +
  lims(y=c(0,1))+
  labs(y="Correlation between Estimates",
       x=NULL,
       title="Correlation amoung Estimates: Level-1 Factor Covariance")+
  scale_color_manual(name="% Admissible", values=cols)+
  theme_bw()+
  theme(panel.grid = element_blank())
p


p <- ggplot(cor.est, aes(x=Cor, y=Est)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(data=filter(cor.est, C90=="< 90%"),
              width=0.3, aes(x=Cor, y=Est, color="< 90%")) +
  geom_jitter(data=filter(cor.est, C90==">= 90%"),
              width=0.3, aes(x=Cor, y=Est, color=">= 90%")) +
  lims(y=c(0,1))+
  labs(y="Correlation between Estimates",
       x=NULL,
       title="Correlation amoung Estimates: Level-1 Factor Covariance",
       subtitle = "Conditional on Level-1 Sample Size")+
  scale_color_manual(name="% Admissible", values=cols)+
  facet_wrap(.~ss_l1)+
  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90))
p


p <- ggplot(cor.est, aes(x=Cor, y=Est)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(data=filter(cor.est, C90=="< 90%"),
              width=0.3, aes(x=Cor, y=Est, color="< 90%")) +
  geom_jitter(data=filter(cor.est, C90==">= 90%"),
              width=0.3, aes(x=Cor, y=Est, color=">= 90%")) +
  lims(y=c(0,1))+
  labs(y="Correlation between Estimates",
       x=NULL,
       title="Correlation amoung Estimates: Level-1 Factor Covariance",
       subtitle = "Conditional on Level-2 Sample Size")+
  scale_color_manual(name="% Admissible", values=cols)+
  facet_wrap(.~ss_l2, nrow=1)+
  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90))
p

p <- ggplot(cor.est, aes(x=Cor, y=Est)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(data=filter(cor.est, C90=="< 90%"),
              width=0.3, aes(x=Cor, y=Est, color="< 90%")) +
  geom_jitter(data=filter(cor.est, C90==">= 90%"),
              width=0.3, aes(x=Cor, y=Est, color=">= 90%")) +
  lims(y=c(0,1))+
  labs(y="Correlation between Estimates",
       x=NULL,
       title="Correlation amoung Estimates: Level-1 Factor Covariance",
       subtitle = "Conditional on Observed Variable ICC")+
  scale_color_manual(name="% Admissible", values=cols)+
  facet_wrap(.~icc_ov)+
  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90))
p

p <- ggplot(cor.est, aes(x=Cor, y=Est)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(data=filter(cor.est, C90=="< 90%"),
              width=0.3, aes(x=Cor, y=Est, color="< 90%")) +
  geom_jitter(data=filter(cor.est, C90==">= 90%"),
              width=0.3, aes(x=Cor, y=Est, color=">= 90%")) +
  lims(y=c(0,1))+
  labs(y="Correlation between Estimates",
       x=NULL,
       title="Correlation amoung Estimates: Level-1 Factor Covariance",
       subtitle = "Conditional on Latent Variable ICC")+
  scale_color_manual(name="% Admissible", values=cols)+
  facet_wrap(.~icc_lv)+
  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90))
p

```



