---
title: "ML-CFA: Convergence and Admissibility Summary"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r init, warning=FALSE, message=FALSE}
rm(list=ls())
source(paste0(getwd(),"/code/load_packages.R"))
source(paste0(getwd(),"/code/get_data.R"))

```

```{r}
sessionInfo()
```


# Convergence

Model converge is when ...

## Single Condition Breakdown

### Estimation Method

```{r}


c <- sim_results %>%
  group_by(Estimator) %>%
  summarise(Converge=mean(Converge))
colnames(c)<- c("Estimation Method", "Convergence")

kable(c, format='html', digits=4) %>%
    kable_styling(full_width = T)

```

### Level-2 Sample Size

```{r}


c <- sim_results %>%
  group_by(ss_l2) %>%
  summarise(Converge=mean(Converge))
colnames(c)<- c("Level-2 N", "Convergence")

kable(c, format='html', digits=4) %>%
    kable_styling(full_width = T)

```

### Level-1 Sample Size

```{r}


c <- sim_results %>%
  group_by(ss_l1) %>%
  summarise(Converge=mean(Converge))
colnames(c)<- c("Level-1 N", "Convergence")

kable(c, format='html', digits=4) %>%
    kable_styling(full_width = T)

```


### ICC *Observed* Variables

```{r}


c <- sim_results %>%
  group_by(icc_ov) %>%
  summarise(Converge=mean(Converge))
colnames(c)<- c("ICC Observed Variable", "Convergence")

kable(c, format='html', digits=4) %>%
    kable_styling(full_width = T)

```

### ICC *Latent* Variables

```{r}


c <- sim_results %>%
  group_by(icc_lv) %>%
  summarise(Converge=mean(Converge))
colnames(c)<- c("ICC Latent Variable", "Convergence")

kable(c, format='html', digits=4) %>%
    kable_styling(full_width = T)

```

## Convergence by Estimation Method and Sample Sizes

### Estimation Method & Level-2 Sample Size

```{r}


c <- sim_results %>%
  group_by(Estimator, ss_l2) %>%
  summarise(Converge=mean(Converge))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'ss_l2', 'Converge')], 
           c[ c$Estimator == 'ULSMV', 'Converge'], 
           c[ c$Estimator == 'WLSMV', 'Converge'])
colnames(c1) <- c('Level-2 N', 'MLR', 'ULSMV', 'WLSMV')


kable(c1, format='html', digits=4) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '= 1, 'Estimation Method'=3))

```

### Estimation Method & Level-1 Sample Size

```{r}


c <- sim_results %>%
  group_by(Estimator, ss_l1) %>%
  summarise(Converge=mean(Converge))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'ss_l1', 'Converge')], 
           c[ c$Estimator == 'ULSMV', 'Converge'], 
           c[ c$Estimator == 'WLSMV', 'Converge'])
colnames(c1) <- c('Level-1 N', 'MLR', 'ULSMV', 'WLSMV')


kable(c1, format='html', digits=4) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '= 1, 'Estimation Method'=3))
```

### Estimation Method, Level-2 Sample Size & Level-1 Sample Size

```{r}


c <- sim_results %>%
  group_by(Estimator, ss_l1, ss_l2) %>%
  summarise(Converge=mean(Converge))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'ss_l1', 'ss_l2', 'Converge')], 
           c[ c$Estimator == 'ULSMV', 'Converge'], 
           c[ c$Estimator == 'WLSMV', 'Converge'])
colnames(c1) <- c('Level-1 N', 'Level-2 N', 'MLR', 'ULSMV', 'WLSMV')


kable(c1, format='html', digits=4) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '= 2, 'Estimation Method'=3))

```



## Across all conditions

```{r}


c <- sim_results %>%
  group_by(Estimator, ss_l1, ss_l2, icc_ov, icc_lv) %>%
  summarise(Converge=mean(Converge))

c1 <- cbind(c[ c$Estimator == 'MLR', c('ss_l2', 'ss_l1', 'icc_ov', 'icc_lv', 'Converge')],
            c[ c$Estimator == 'ULSMV', 'Converge'],
            c[ c$Estimator == 'WLSMV', 'Converge'])
colnames(c1) <- c('Level-2 N', 'Level-1 N', 'ICC-OV', 'ICC-LV', 'MLR', 'ULSMV', 'WLSMV')


kable(c1, format='html', digits=4) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '= 4, 'Estimation Method'=3))

```



# Admissibility Summary

Admissibility rates are first subsetted to the converged models. 
So, the rates may seem misleading and not directly relatable across all conditions and models due to differences in convergence rates.

```{r}

c.sim_results <- filter(sim_results, Converge == 1)

```

## Single Condition Breakdown

### Estimation Method

```{r}


c <- c.sim_results %>%
  group_by(Estimator) %>%
  summarise(Admissible=mean(Admissible))
colnames(c)<- c("Estimation Method", "Admissible")

kable(c, format='html', digits=4) %>%
    kable_styling(full_width = T)

```

### Level-2 Sample Size

```{r}


c <- c.sim_results %>%
  group_by(ss_l2) %>%
  summarise(Admissible=mean(Admissible))
colnames(c)<- c("Level-2 N", "Admissible")

kable(c, format='html', digits=4) %>%
    kable_styling(full_width = T)

```

### Level-1 Sample Size

```{r}


c <- c.sim_results %>%
  group_by(ss_l1) %>%
  summarise(Admissible=mean(Admissible))
colnames(c)<- c("Level-1 N", "Admissible")

kable(c, format='html', digits=4) %>%
    kable_styling(full_width = T)

```


### ICC *Observed* Variables

```{r}


c <- c.sim_results %>%
  group_by(icc_ov) %>%
  summarise(Admissible=mean(Admissible))
colnames(c)<- c("ICC Observed Variable", "Admissible")

kable(c, format='html', digits=4) %>%
    kable_styling(full_width = T)

```

### ICC *Latent* Variables

```{r}


c <- c.sim_results %>%
  group_by(icc_lv) %>%
  summarise(Admissible=mean(Admissible))
colnames(c)<- c("ICC Latent Variable", "Admissible")

kable(c, format='html', digits=4) %>%
    kable_styling(full_width = T)

```

## Admissible Replications by Estimation Method and Sample Sizes

### Estimation Method & Level-2 Sample Size

```{r}


c <- c.sim_results %>%
  group_by(Estimator, ss_l2) %>%
  summarise(Admissible=mean(Admissible))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'ss_l2', 'Admissible')], 
           c[ c$Estimator == 'ULSMV', 'Admissible'], 
           c[ c$Estimator == 'WLSMV', 'Admissible'])
colnames(c1) <- c('Level-2 N', 'MLR', 'ULSMV', 'WLSMV')

kable(c1, format='html', digits=4) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '= 1, 'Estimation Method'=3))

```

### Estimation Method & Level-1 Sample Size

```{r}

c <- c.sim_results %>%
  group_by(Estimator, ss_l1) %>%
  summarise(Admissible=mean(Admissible))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'ss_l1', 'Admissible')], 
           c[ c$Estimator == 'ULSMV', 'Admissible'], 
           c[ c$Estimator == 'WLSMV', 'Admissible'])
colnames(c1) <- c('Level-1 N', 'MLR', 'ULSMV', 'WLSMV')

kable(c1, format='html', digits=4) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '= 1, 'Estimation Method'=3))
```

### Estimation Method, Level-2 Sample Size & Level-1 Sample Size

```{r}


c <- c.sim_results %>%
  group_by(Estimator, ss_l1, ss_l2) %>%
  summarise(Admissible=mean(Admissible))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'ss_l1', 'ss_l2', 'Admissible')], 
           c[ c$Estimator == 'ULSMV', 'Admissible'], 
           c[ c$Estimator == 'WLSMV', 'Admissible'])
colnames(c1) <- c('Level-1 N', 'Level-2 N', 'MLR', 'ULSMV', 'WLSMV')

kable(c1, format='html', digits=4) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '= 2, 'Estimation Method'=3))

```

## Admissible Replications for individual conditions

```{r}


c <- c.sim_results %>%
  group_by(Estimator, ss_l1, ss_l2, icc_ov, icc_lv) %>%
  summarise(Admissible=mean(Admissible))

c1 <- cbind(c[ c$Estimator == 'MLR', c('ss_l2', 'ss_l1', 'icc_ov', 'icc_lv', 'Admissible')],
            c[ c$Estimator == 'ULSMV', 'Admissible'],
            c[ c$Estimator == 'WLSMV', 'Admissible'])
colnames(c1) <- c('Level-2 N', 'Level-1 N', 'ICC-OV', 'ICC-LV', 'MLR', 'ULSMV', 'WLSMV')


kable(c1, format='html', digits=4) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '= 4, 'Estimation Method'=3))

```


# Manuscript Table(s)

```{r man-table}


c <- sim_results %>%
  group_by(Estimator, ss_l2) %>%
  mutate(A = ifelse(is.na(Admissible), 0, Admissible)) %>%
  summarise(Admissible=mean(A, na.rm = T))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'ss_l2','Admissible')], 
           c[ c$Estimator == 'ULSMV', 'Admissible'], 
           c[ c$Estimator == 'WLSMV', 'Admissible'])
colnames(c1) <- c('Level-2 N_2', 'MLR', 'ULSMV', 'WLSMV')


kable(c1, format='html', digits=3) %>%
  kable_styling(full_width = T)


print(xtable(c1, digits = 3,align=c("l", "l", "r", "r", "r"),
             display=c("s", "d", "f", "f", "f"),
             caption="Rates of admissible replications",
             label="tb:admiss"),
      booktabs = T, include.rownames = F,
      caption.placement = "top")


# Version 2
c <- sim_results %>%
  group_by(Estimator, ss_l2, ss_l1) %>%
  mutate(A = ifelse(is.na(Admissible), 0, Admissible)) %>%
  summarise(Admissible=mean(A, na.rm = T))

c1 <- cbind(c[ c$Estimator == 'MLR', c('ss_l2', 'ss_l1', 'Admissible')], 
           c[ c$Estimator == 'ULSMV', 'Admissible'], 
           c[ c$Estimator == 'WLSMV', 'Admissible'])
colnames(c1) <- c('Level-2 N_2', "Level-1 N_1", 'MLR', 'ULSMV', 'WLSMV')


kable(c1, format='html', digits=3) %>%
  kable_styling(full_width = T)


print(xtable(c1, digits = 3,align=c("l", "l","l", "r", "r", "r"),
             display=c("s","s", "d", "f", "f", "f"),
             caption="Convergence rates indicate problems for all estimation methods",
             label="tb:admiss"),
      booktabs = T, include.rownames = F,
      caption.placement = "top")

```