---
title: "ML-CFA: Parameter Relative Bias"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r init, warning=FALSE, message=FALSE}
rm(list=ls())
source(paste0(getwd(),"/code/load_packages.R"))
source(paste0(getwd(),"/code/get_data.R"))


```

```{r}
sessionInfo()

# general options
theme_set(theme_bw())
options(digits=3)
```


# Bias


Bias estimated were computed for 

1. Factor loadings ($\lambda_{1-10}$),
2. Level-1 factor covariance ($\psi_{W12}$),
3. Level-2 factor (co)variances ($\psi_{B1}, \psi_{B2}, \psi_{B12}$),
4. Level-2 item residual variances ($\theta_{B1-10}$), and
5. ICCs for latent and observed variable

with special attention on the ICCs because these tend to be important metrics in ML-CFA as an indication of the need for ML-CFA/multilevel modeling in general.
If we are unable to precisely recapture the level of effect that the multilevel structure has on the observed responses, then the model is ill-performing.
We assessed the performance using three metrics of bias.

1. Relative Bias - average deviation of the estimates ($\hat{\theta}$) from the known population value ($\theta$) across replications.
\[
Bias(\hat{\theta}) = \sum_{j=1}^{n_r}\left(\frac{\hat{\theta}_j- \theta}{\theta}\right)/n_r\times 100
\]
where,
$n_r$ is the number of usable replications in the cell of the design.
However, another representation of bias was also of interest, namely, the root mean square error (RMSE).
We partitioned RMSE the that is the average bias (AB) and the sampling variability (SV) (Harwell, 2018).
\[
RMSE(\hat\theta) = \sum_{j=1}^{n_r}\frac{(\hat\theta_j -\theta)^2}{n_r}= {\left(\bar{\hat\theta} - \theta\right)}^2 +  \sum_{j=1}^{n_r}\frac{(\hat\theta_j -\bar{\hat\theta})^2}{n_r}
\]
where,
$\bar{\hat\theta}$ is the average estimate of the parameter of interest,
${\left(\bar{\hat\theta} - \theta\right)}^2$ is the squared bias of the estimate, and
$\sum_{j=1}^{n_r}\frac{(\hat\theta_j -\bar{\hat\theta})^2}{n_r}$ represents the SV (sampling variability) of the estimates.
Partitioning the bias into these two pieces allows us to assess RMSE based on the two parts of potential sources of error (i.e., bias versus sampling variability).
If all the variability in RMSE is due to bias, then all estimates of $\hat\theta$ are equal, but if all variabilityin RMSE is due to sampling variability, then RMSE is equal to the sampling variability.
Therefore, the three values are reported here (but only the two parititioned components in the manuscript to save space).

## Estimation Method Efficiency

Another aspect of the parameter estimates that was of interest was the variability in estimation between estimation methods.
Meaning, which estimation method was least variable relative to the other methods.
We compute an efficiency ratio (or relative efficiency) between estimation methods (m = MLR, u = ULSMV, and w = WLSMV).
\[
RE = \sqrt{\left(\frac{\sum_{\forall j}(\hat{\theta}_{mj}-\theta)^2}{\sum_{\forall j}(\hat{\theta}_{uj}-\theta)^2}\right)}
\]
where RE = relative efficiency,
and the ratio was computed for all three pairwise comparisons of (m, u, w).

# Computing bias and efficiency estimates

Here, we estimated the bias estimates.

First, we set up some functions to compute the values of interest.

```{r}
#compute RB
# p = parameter estimate of interest
# pt = true value of parameter of interest
est_relative_bias <- function(data, p, pt){
  nr <- nrow(data)
  data[, pt] <- as.numeric(data[,pt])
  
  rb <- sum((data[, p] - data[, pt])/data[,pt], na.rm = T)/nr*100
  names(rb) <- 'RB'
  return(rb)
}

# compute RMSE components
est_rmse <- function(data, p, pt){
  nr <- nrow(data)
  data[, pt] <- as.numeric(data[,pt])
  
  est_a <- mean(data[,p], na.rm = T)
  bias <- (est_a - data[,pt][1])**2
  sv <- sum((data[, p] - est_a)**2, na.rm=T)/nr
  rmse <- bias + sv
  out <- c(rmse, bias, sv)
  names(out) <- c('RMSE', 'Bias', 'SampVar')
  return(out)
}

# compute estimated relative efficiency of 
#  parameter est between two estimation methods
est_relative_efficiency <- function(data, p, pt, est1, est2){
  dat1 <- filter(data, Estimator == est1)
  dat2 <- filter(data, Estimator == est2)
  dat1[,pt] <- as.numeric(dat1[,pt])
  dat2[,pt] <- as.numeric(dat2[,pt])
  re <- sqrt(sum( (dat1[, p] - dat1[,pt])**2, na.rm=T)/sum( (dat2[, p] - dat2[pt])**2, na.rm=T))
  names(re) <- 'RE'
  return(re)
}


```

## Running Computations

Next, loop through the desired results to get the estimates of bias of interest.
For more details on the naming of variables for the true values, see the [Data Cleaning](data-cleaning.html) page.

```{r get-res, eval=F}

# take out unconverged/inadmissible cases
sim_results <- filter(sim_results, Converge==1, Admissible==1)

# set up vectors of variable names
pvec <- c(paste0('lambda1',1:6), paste0('lambda2',6:10), 'psiW12','psiB1', 'psiB2', 'psiB12', paste0('thetaB',1:10), 'icc_lv1_est', 'icc_lv2_est', paste0('icc_ov',1:10,'_est'))
# stored "true" values of parameters by each condition
ptvec <- c(rep('lambdaT',11), 'psiW12T', 'psiB1T', 'psiB2T', 'psiB12T', rep("thetaBT", 10), rep('icc_lv',2), rep('icc_ov',10))

# iterators - conditions
N1 <- unique(sim_results$ss_l1)
N2 <- unique(sim_results$ss_l2)
ICC_LV <- unique(sim_results$icc_lv)
ICC_OV <- unique(sim_results$icc_ov)
EST <- levels(sim_results$Estimator)

# results matrix
result <- data.frame(matrix(nrow=length(N1)*length(N2)*length(ICC_LV)*length(ICC_OV)*length(pvec)*length(EST), ncol=(16)))
colnames(result) <- c('N1', 'N2', 'ICC_LV' ,'ICC_OV', 'Variable', 'Estimator', 'RB', 'RMSE', 'Bias', 'SampVar', 'muRE', 'mwRE', 'uwRE', 'nRep', 'estMean', 'estSD')

j <- 1 # row id
for(n1 in N1){
  for(n2 in N2){
    for(iccl in ICC_LV){
      for(icco in ICC_OV){
        for(i in 1:length(pvec)){
            
            dat <- filter(sim_results, ss_l1 == n1, ss_l2==n2,
                          icc_lv==iccl, icc_ov==icco)
            result[j:(j+2), 1:5] <- matrix(rep(c(n1,n2, iccl,icco, pvec[i]),3),
                                           ncol=5, byrow = T)
              
              # compute bias by each estimation method
              k <- 0
              for(est in EST){
                sdat <- filter(dat, Estimator==est)
                result[j+k, 6] <- est
                result[j+k, 7] <- est_relative_bias(sdat, pvec[i], ptvec[i])
                result[j+k, 8:10] <- est_rmse(sdat, pvec[i], ptvec[i])
                result[j+k, 14] <- nrow(sdat) # number of converged replications
                result[j+k, 15] <- mean(sdat[, pvec[i]])
                result[j+k, 16] <- sd(sdat[, pvec[i]])
                k<-k+1
              }
              # Compute Relative Efficiency
              # MLR vs. ULSMV
              result[j:(j+2), 11] <- est_relative_efficiency(dat, pvec[i], ptvec[i],
                                                       'MLR','ULSMV')
              # MLR vs. WLSMV
              result[j:(j+2), 12] <- est_relative_efficiency(dat, pvec[i], ptvec[i],
                                                       'MLR','WLSMV')
              # ULSMV vs. WLSMV
              result[j:(j+2), 13] <- est_relative_efficiency(dat, pvec[i], ptvec[i],
                                                       'ULSMV','WLSMV')
              
          # update row
          j <- j+3
        }
      }
    }
  }
}


# Save Results
write_csv(result, path=paste0(w.d, "/data/results_bias_est.csv"))

# remove sim_results since not-needed anymore
remove(sim_results, dat, sdat, icc_est)


```

So, there are a lot of results that could be reported from this matrix of results.
We have saved these results and these estimates are included in the accompanying Shiny app for more detailed exploration by those interested.
Here, we describe a subset of the results that we feelt are most important.

```{r read-data-back-in, include=F}
# set up vectors of variable names
pvec <- c(paste0('lambda1',1:6), paste0('lambda2',6:10), 'psiW12','psiB1', 'psiB2', 'psiB12', paste0('thetaB',1:10), 'icc_lv1_est', 'icc_lv2_est', paste0('icc_ov',1:10,'_est'))
# stored "true" values of parameters by each condition
ptvec <- c(rep('lambdaT',11), 'psiW12T', 'psiB1T', 'psiB2T', 'psiB12T', rep("thetaBT", 10), rep('icc_lv',2), rep('icc_ov',10))

result <- read_csv(paste0(w.d, "/data/results_bias_est.csv"))

# levels of categorical values

result <- result %>%
  mutate(N1 = factor(N1, c("5", "10", "30")),
         N2 = factor(N2, c("30", "50", "100", "200")),
         ICC_OV = factor(ICC_OV, c("0.1","0.3", "0.5")),
         ICC_LV = factor(ICC_LV, c("0.1", "0.5")))
# result <- result %>%
#   mutate(N1 = fct_relevel(N1, c("5", "10", "30")),
#          N2 = fct_relevel(N2, c("30", "50", "100", "200")),
#          ICC_OV = fct_relevel(ICC_OV, c("0.1","0.3", "0.5")),
#          ICC_LV = fct_relevel(ICC_LV, c("0.1", "0.5")))

```


# Summarizing Results

First, we will plot estimates (botxplots) to show how these estimates changed across conditions.
To summarize the results we will average over the parameters that only differ y indices.
Meaning we will describe the "average factor loading bias" by reporting the average bias for factor loadings.
Additionally, different conditions resultedin different "sample sizes."
By this we mean the number of uses replications.
The different number of cases per condition was accounted for by creating a "weight" variable for each row of the `result` object.
This meant that conditions that had more usable replications counted more towards to averages reported (or count as much as if we averaged over the individual replications).

```{r}

result$wi <- result$nRep/500
# 500 is the max number of replications per cell

```

## Factor loadings

```{r}

sdat <- filter(result, Variable %like% 'lambda')

# first, plot estimates
p1 <- ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  geom_hline(yintercept = 0.6, color="red")+
  labs(y="Average Factor Loading")

p2 <- ggplot(sdat, aes(y=estSD))+
  geom_boxplot()+
  labs(y="SD of Factor Loadings")

p3 <- ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias")

p4 <- ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error")

p5 <- ggplot(sdat, aes(y=Bias))+
  geom_boxplot()+
  labs(y="Sqaured Bias")

p6 <- ggplot(sdat, aes(y=SampVar))+
  geom_boxplot()+
  labs(y="Sampling Variance of Estimates")


p <- (p1 + p2 + p3)/(p4 + p5 + p6)
p

```

## Single Condition Breakdown

### Estimation Method

```{r}

ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  geom_hline(yintercept = 0.6, color="red")+
  labs(y="Average Factor Loading")+
  facet_wrap(.~Estimator)

ggplot(sdat, aes(y=estSD))+
  geom_boxplot()+
  labs(y="SD of Factor Loadings")+
  facet_wrap(.~Estimator)

ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias")+
  facet_wrap(.~Estimator)

ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error")+
  facet_wrap(.~Estimator)

ggplot(sdat, aes(y=Bias))+
  geom_boxplot()+
  labs(y="Sqaured Bias")+
  facet_wrap(.~Estimator)

ggplot(sdat, aes(y=SampVar))+
  geom_boxplot()+
  labs(y="Sampling Variance of Estimates")+
  facet_wrap(.~Estimator)


c <- sdat %>%
  group_by(Estimator) %>%
  summarise(est = weighted.mean(estMean, wi),
            RB = weighted.mean(RB, wi),
            RMSE = weighted.mean(RMSE, wi),
            Bias = weighted.mean(Bias, wi),
            SampVar =weighted.mean(SampVar, wi))

kable(c, format='html', digits=3) %>%
  kable_styling(full_width = T)

```

### Level-2 Sample Size

```{r}

ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  geom_hline(yintercept = 0.6, color="red")+
  labs(y="Average Factor Loading")+
  facet_wrap(.~N2)

ggplot(sdat, aes(y=estSD))+
  geom_boxplot()+
  labs(y="SD of Factor Loadings")+
  facet_wrap(.~N2)

ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias")+
  facet_wrap(.~N2)

ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error")+
  facet_wrap(.~N2)

ggplot(sdat, aes(y=Bias))+
  geom_boxplot()+
  labs(y="Sqaured Bias")+
  facet_wrap(.~N2)

ggplot(sdat, aes(y=SampVar))+
  geom_boxplot()+
  labs(y="Sampling Variance of Estimates")+
  facet_wrap(.~N2)


c <- sdat %>%
  group_by(N2) %>%
  summarise(est = weighted.mean(estMean, wi),
            RB = weighted.mean(RB, wi),
            RMSE = weighted.mean(RMSE, wi),
            Bias = weighted.mean(Bias, wi),
            SampVar =weighted.mean(SampVar, wi))

kable(c, format='html', digits=3) %>%
  kable_styling(full_width = T)

```

### Level-1 Sample Size

```{r}

ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  geom_hline(yintercept = 0.6, color="red")+
  labs(y="Average Factor Loading")+
  facet_wrap(.~N1)

ggplot(sdat, aes(y=estSD))+
  geom_boxplot()+
  labs(y="SD of Factor Loadings")+
  facet_wrap(.~N1)

ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias")+
  facet_wrap(.~N1)

ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error")+
  facet_wrap(.~N1)

ggplot(sdat, aes(y=Bias))+
  geom_boxplot()+
  labs(y="Sqaured Bias")+
  facet_wrap(.~N1)

ggplot(sdat, aes(y=SampVar))+
  geom_boxplot()+
  labs(y="Sampling Variance of Estimates")+
  facet_wrap(.~N1)


c <- sdat %>%
  group_by(N1) %>%
  summarise(est = weighted.mean(estMean, wi),
            RB = weighted.mean(RB, wi),
            RMSE = weighted.mean(RMSE, wi),
            Bias = weighted.mean(Bias, wi),
            SampVar =weighted.mean(SampVar, wi))

kable(c, format='html', digits=3) %>%
  kable_styling(full_width = T)

```


### ICC *Observed* Variables

```{r}

ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  geom_hline(yintercept = 0.6, color="red")+
  labs(y="Average Factor Loading")+
  facet_wrap(.~ICC_OV)

ggplot(sdat, aes(y=estSD))+
  geom_boxplot()+
  labs(y="SD of Factor Loadings")+
  facet_wrap(.~ICC_OV)

ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias")+
  facet_wrap(.~ICC_OV)

ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error")+
  facet_wrap(.~ICC_OV)

ggplot(sdat, aes(y=Bias))+
  geom_boxplot()+
  labs(y="Sqaured Bias")+
  facet_wrap(.~ICC_OV)

ggplot(sdat, aes(y=SampVar))+
  geom_boxplot()+
  labs(y="Sampling Variance of Estimates")+
  facet_wrap(.~ICC_OV)


c <- sdat %>%
  group_by(ICC_OV) %>%
  summarise(est = weighted.mean(estMean, wi),
            RB = weighted.mean(RB, wi),
            RMSE = weighted.mean(RMSE, wi),
            Bias = weighted.mean(Bias, wi),
            SampVar =weighted.mean(SampVar, wi))

kable(c, format='html', digits=3) %>%
  kable_styling(full_width = T)

```

### ICC *Latent* Variables

```{r}

ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  geom_hline(yintercept = 0.6, color="red")+
  labs(y="Average Factor Loading")+
  facet_wrap(.~ICC_LV)

ggplot(sdat, aes(y=estSD))+
  geom_boxplot()+
  labs(y="SD of Factor Loadings")+
  facet_wrap(.~ICC_LV)

ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias")+
  facet_wrap(.~ICC_LV)

ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error")+
  facet_wrap(.~ICC_LV)

ggplot(sdat, aes(y=Bias))+
  geom_boxplot()+
  labs(y="Sqaured Bias")+
  facet_wrap(.~ICC_LV)

ggplot(sdat, aes(y=SampVar))+
  geom_boxplot()+
  labs(y="Sampling Variance of Estimates")+
  facet_wrap(.~ICC_LV)


c <- sdat %>%
  group_by(ICC_LV) %>%
  summarise(est = weighted.mean(estMean, wi),
            RB = weighted.mean(RB, wi),
            RMSE = weighted.mean(RMSE, wi),
            Bias = weighted.mean(Bias, wi),
            SampVar =weighted.mean(SampVar, wi))

kable(c, format='html', digits=3) %>%
  kable_styling(full_width = T)

```

## Convergence by Estimation Method and Sample Sizes

### Estimation Method & Level-2 Sample Size

```{r}

ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  geom_hline(yintercept = 0.6, color="red")+
  labs(y="Average Factor Loading")+
  facet_grid(N2~Estimator)

ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias")+
  facet_grid(N2~Estimator)

ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error")+
  facet_grid(N2~Estimator)

c <- sdat %>%
  group_by(Estimator, N2) %>%
  summarise(est = weighted.mean(estMean, wi),
            RB = weighted.mean(RB, wi),
            RMSE = weighted.mean(RMSE, wi),
            Bias = weighted.mean(Bias, wi),
            SampVar =weighted.mean(SampVar, wi))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2', 'est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'ULSMV', c('est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'WLSMV', c('est', 'RB', 'RMSE')])
colnames(c1) <- c('N2',  rep(c('est', 'RB', 'RMSE'), 3))

kable(c1, format='html', digits=3, row.names = F) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '=1, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3))

```

### Estimation Method & Level-1 Sample Size

```{r}

ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  geom_hline(yintercept = 0.6, color="red")+
  labs(y="Average Factor Loading")+
  facet_grid(N1~Estimator)

ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias")+
  facet_grid(N1~Estimator)

ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error")+
  facet_grid(N1~Estimator)

c <- sdat %>%
  group_by(Estimator, N1) %>%
  summarise(est = weighted.mean(estMean, wi),
            RB = weighted.mean(RB, wi),
            RMSE = weighted.mean(RMSE, wi),
            Bias = weighted.mean(Bias, wi),
            SampVar =weighted.mean(SampVar, wi))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N1', 'est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'ULSMV', c('est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'WLSMV', c('est', 'RB', 'RMSE')])
colnames(c1) <- c('N1',  rep(c('est', 'RB', 'RMSE'), 3))

kable(c1, format='html', digits=3, row.names = F) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '=1, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3))
```

### Estimation Method, Level-2 Sample Size & Level-1 Sample Size

```{r}

ggplot(sdat, aes(y=estMean,x=N1, group=N1))+
  geom_boxplot()+
  geom_hline(yintercept = 0.6, color="red")+
  labs(y="Average Factor Loading")+
  facet_grid(N2~Estimator)

ggplot(sdat, aes(y=RB,x=N1, group=N1))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias")+
  facet_grid(N2~Estimator)

ggplot(sdat, aes(y=RMSE,x=N1, group=N1))+
  geom_boxplot()+
  labs(y="Root Mean Square Error")+
  facet_grid(N2~Estimator)

c <- sdat %>%
  group_by(Estimator, N2, N1) %>%
  summarise(est = weighted.mean(estMean, wi),
            RB = weighted.mean(RB, wi),
            RMSE = weighted.mean(RMSE, wi),
            Bias = weighted.mean(Bias, wi),
            SampVar =weighted.mean(SampVar, wi))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2','N1', 'est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'ULSMV', c('est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'WLSMV', c('est', 'RB', 'RMSE')])
colnames(c1) <- c('N2','N1',  rep(c('est', 'RB', 'RMSE'), 3))

kable(c1, format='html', digits=3, row.names = F) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '=2, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3))

```





<!-- ## Extracted Results -->

<!-- Here, we subset the large results matrix above to the following parameters: -->

<!-- 1. Item 1 and item 6 parameters (factor loadings, residual L2 variances, ICCs) -->
<!-- 2. Level-2 latent variable covariance matrix -->
<!-- 3. ICC Latent Variables -->

<!-- Tables will be reported by level-2 sample size ($N_2$) condition (4 tables) for *better* readability. -->

<!-- ```{r} -->
<!-- keepVar <- c('lambda11', 'lambda16', 'lambda26', 'thetaB1', 'thetaB6', 'icc_ov1_est',  'icc_ov6_est', 'psiB1', 'psiB2', 'psiB12', 'icc_lv1_est', 'icc_lv2_est') -->
<!-- subresults <- filter(result, Variable %in% keepVar) -->

<!-- ``` -->

<!-- A very high-level description of the bias can be seen with a side-by-side boxplots of RB by parameter for each of the estimation methods. -->

<!-- ```{r} -->

<!-- ggplot(subresults, aes(y=RB, x=Estimator, color=Estimator)) + -->
<!--   geom_boxplot(outlier.alpha = 0.5) + -->
<!--   lims(y=c(-150,150)) + -->
<!--   labs(title='Comparing Relative Bias', x="", y="Relative Bias") + -->
<!--   facet_wrap(~Variable)+ -->
<!--   theme_bw()+ -->
<!--   theme(axis.text.x = element_text(angle = 45, hjust=1), -->
<!--         legend.position = 'none') -->

<!-- ``` -->


<!-- ### Sample size: $N_2=30$ -->

<!-- ```{r} -->

<!-- subres <- filter(subresults, N2=="30") -->
<!-- kable(subres, format='html', digits=3)%>% -->
<!--   kable_styling(full_width = T) -->

<!-- ggplot(subres, aes(y=RB, x=Estimator, color=Estimator)) + -->
<!--   geom_boxplot(outlier.alpha = 0.5) + -->
<!--   lims(y=c(-150,150)) + -->
<!--   labs(title='Comparing Relative Bias', x="", y="Relative Bias") + -->
<!--   facet_wrap(~Variable)+ -->
<!--   theme_bw()+ -->
<!--   theme(axis.text.x = element_text(angle = 45, hjust=1), -->
<!--         legend.position = 'none') -->

<!-- ``` -->

<!-- ### Sample size: $N_2=50$ -->

<!-- ```{r} -->

<!-- subres <- filter(subresults, N2=="50") -->
<!-- kable(subres, format='html', digits=3)%>% -->
<!--   kable_styling(full_width = T) -->

<!-- ggplot(subres, aes(y=RB, x=Estimator, color=Estimator)) + -->
<!--   geom_boxplot(outlier.alpha = 0.5) + -->
<!--   lims(y=c(-150,150)) + -->
<!--   labs(title='Comparing Relative Bias', x="", y="Relative Bias") + -->
<!--   facet_wrap(~Variable)+ -->
<!--   theme_bw()+ -->
<!--   theme(axis.text.x = element_text(angle = 45, hjust=1), -->
<!--         legend.position = 'none') -->

<!-- ``` -->


<!-- ### Sample size: $N_2=100$ -->

<!-- ```{r} -->

<!-- subres <- filter(subresults, N2=="100") -->
<!-- kable(subres, format='html', digits=3)%>% -->
<!--   kable_styling(full_width = T) -->

<!-- ggplot(subres, aes(y=RB, x=Estimator, color=Estimator)) + -->
<!--   geom_boxplot(outlier.alpha = 0.5) + -->
<!--   lims(y=c(-150,150)) + -->
<!--   labs(title='Comparing Relative Bias', x="", y="Relative Bias") + -->
<!--   facet_wrap(~Variable)+ -->
<!--   theme_bw()+ -->
<!--   theme(axis.text.x = element_text(angle = 45, hjust=1), -->
<!--         legend.position = 'none') -->

<!-- ``` -->

<!-- ### Sample size: $N_2=200$ -->

<!-- ```{r} -->

<!-- subres <- filter(subresults, N2=="200") -->
<!-- kable(subres, format='html', digits=3)%>% -->
<!--   kable_styling(full_width = T) -->

<!-- ggplot(subres, aes(y=RB, x=Estimator, color=Estimator)) + -->
<!--   geom_boxplot(outlier.alpha = 0.5) + -->
<!--   lims(y=c(-150,150)) + -->
<!--   labs(title='Comparing Relative Bias', x="", y="Relative Bias") + -->
<!--   facet_wrap(~Variable)+ -->
<!--   theme_bw()+ -->
<!--   theme(axis.text.x = element_text(angle = 45, hjust=1), -->
<!--         legend.position = 'none') -->

<!-- ``` -->


<!-- ## Tables -->

<!-- ### Factor loading (item-1) -->

<!-- ```{r} -->
<!-- result$wi <- result$nRep/500 -->

<!-- sdat <- filter(result, Variable=='lambda11') -->

<!-- c <- sdat %>% -->
<!--   group_by(Estimator, N2, N1) %>% -->
<!--   summarise(est = weighted.mean(estMean, wi), -->
<!--             RB = weighted.mean(RB, wi), -->
<!--             RMSE = weighted.mean(RMSE, wi), -->
<!--             Bias = weighted.mean(Bias, wi), -->
<!--             SampVar =weighted.mean(SampVar, wi)) -->

<!-- c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2', 'N1', 'est', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'ULSMV', c('est', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'WLSMV', c('est', 'RB', 'RMSE')]) -->
<!-- colnames(c1) <- c('N2', 'N1', rep(c('est', 'RB', 'RMSE'), 3)) -->

<!-- kable(c1, format='html', digits=3, row.names = F) %>% -->
<!--   kable_styling(full_width = T) %>% -->
<!--   add_header_above(c(' '=2, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3)) -->
<!-- ## Print out in tex -->
<!-- print(xtable(c1, digits = 3), booktabs = T, include.rownames = F) -->


<!-- # all factors -->
<!-- c <- sdat -->

<!-- c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2', 'N1', 'ICC_OV', 'ICC_LV', 'estMean', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'ULSMV', c('estMean', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'WLSMV', c('estMean', 'RB', 'RMSE')]) -->
<!-- colnames(c1) <- c('N2', 'N1','ICC_OV', 'ICC_LV', rep(c('est', 'RB', 'RMSE'), 3)) -->

<!-- kable(c1, format='html', digits=3, row.names = F) %>% -->
<!--   kable_styling(full_width = T) %>% -->
<!--   add_header_above(c(' '=4, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3)) -->
<!-- ## Print out in tex -->
<!-- print(xtable(c1, digits = 3), booktabs = T, include.rownames = F) -->


<!-- ``` -->

<!-- ### Level-2 Factor Variance -->

<!-- ```{r} -->

<!-- sdat <- filter(result, Variable=='psiB1', ICC_LV==0.5) -->
<!-- c <- sdat %>% -->
<!--   group_by(Estimator, N2, N1) %>% -->
<!--   summarise(est = weighted.mean(estMean, wi), -->
<!--             RB = weighted.mean(RB, wi), -->
<!--             RMSE = weighted.mean(RMSE, wi), -->
<!--             Bias = weighted.mean(Bias, wi), -->
<!--             SampVar =weighted.mean(SampVar, wi)) -->
<!-- c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2', 'N1', 'est', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'ULSMV', c('est', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'WLSMV', c('est', 'RB', 'RMSE')]) -->
<!-- colnames(c1) <- c('N2', 'N1', rep(c('est', 'RB', 'RMSE'), 3)) -->
<!-- kable(c1, format='html', digits=3, row.names = F) %>% -->
<!--   kable_styling(full_width = T) %>% -->
<!--   add_header_above(c(' '=2, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3)) -->
<!-- ## Print out in tex -->
<!-- print(xtable(c1, digits=3), booktabs = T, include.rownames = F) -->

<!-- sdat <- filter(result, Variable=='psiB1', ICC_LV==0.1) -->

<!-- c <- sdat %>% -->
<!--   group_by(Estimator, N2, N1) %>% -->
<!--   summarise(est = weighted.mean(estMean, wi), -->
<!--             RB = weighted.mean(RB, wi), -->
<!--             RMSE = weighted.mean(RMSE, wi), -->
<!--             Bias = weighted.mean(Bias, wi), -->
<!--             SampVar =weighted.mean(SampVar, wi)) -->

<!-- c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2', 'N1', 'est', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'ULSMV', c('est', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'WLSMV', c('est', 'RB', 'RMSE')]) -->
<!-- colnames(c1) <- c('N2', 'N1', rep(c('est', 'RB', 'RMSE'), 3)) -->


<!-- kable(c1, format='html', digits=3, row.names = F) %>% -->
<!--   kable_styling(full_width = T) %>% -->
<!--   add_header_above(c(' '=2, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3)) -->
<!-- ## Print out in tex -->
<!-- print(xtable(c1, digits=3), booktabs = T, include.rownames = F) -->

<!-- # all factors -->
<!-- sdat <- filter(result, Variable=='psiB1') -->
<!-- c <- sdat -->

<!-- c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2', 'N1', 'ICC_OV', 'ICC_LV', 'estMean', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'ULSMV', c('estMean', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'WLSMV', c('estMean', 'RB', 'RMSE')]) -->
<!-- colnames(c1) <- c('N2', 'N1','ICC_OV', 'ICC_LV', rep(c('est', 'RB', 'RMSE'), 3)) -->

<!-- kable(c1, format='html', digits=3, row.names = F) %>% -->
<!--   kable_styling(full_width = T) %>% -->
<!--   add_header_above(c(' '=4, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3)) -->
<!-- ## Print out in tex -->
<!-- print(xtable(c1, digits = 3), booktabs = T, include.rownames = F) -->
<!-- # find extreme cases -->


<!-- ``` -->

<!-- ### Level-2 Factor Covariance -->

<!-- ```{r} -->



<!-- sdat <- filter(result, Variable=='psiB12', ICC_LV==0.5) -->
<!-- c <- sdat %>% -->
<!--   group_by(Estimator, N2, N1) %>% -->
<!--   summarise(est = weighted.mean(estMean, wi), -->
<!--             RB = weighted.mean(RB, wi), -->
<!--             RMSE = weighted.mean(RMSE, wi), -->
<!--             Bias = weighted.mean(Bias, wi), -->
<!--             SampVar =weighted.mean(SampVar, wi)) -->
<!-- c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2', 'N1', 'est', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'ULSMV', c('est', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'WLSMV', c('est', 'RB', 'RMSE')]) -->
<!-- colnames(c1) <- c('N2', 'N1', rep(c('est', 'RB', 'RMSE'), 3)) -->
<!-- kable(c1, format='html', digits=3, row.names = F) %>% -->
<!--   kable_styling(full_width = T) %>% -->
<!--   add_header_above(c(' '=2, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3)) -->
<!-- ## Print out in tex -->
<!-- print(xtable(c1, digits=3), booktabs = T, include.rownames = F) -->

<!-- sdat <- filter(result, Variable=='psiB12', ICC_LV==0.1) -->

<!-- c <- sdat %>% -->
<!--   group_by(Estimator, N2, N1) %>% -->
<!--   summarise(est = weighted.mean(estMean, wi), -->
<!--             RB = weighted.mean(RB, wi), -->
<!--             RMSE = weighted.mean(RMSE, wi), -->
<!--             Bias = weighted.mean(Bias, wi), -->
<!--             SampVar =weighted.mean(SampVar, wi)) -->

<!-- c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2', 'N1', 'est', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'ULSMV', c('est', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'WLSMV', c('est', 'RB', 'RMSE')]) -->
<!-- colnames(c1) <- c('N2', 'N1', rep(c('est', 'RB', 'RMSE'), 3)) -->


<!-- kable(c1, format='html', digits=3, row.names = F) %>% -->
<!--   kable_styling(full_width = T) %>% -->
<!--   add_header_above(c(' '=2, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3)) -->
<!-- ## Print out in tex -->
<!-- print(xtable(c1, digits=3), booktabs = T, include.rownames = F) -->

<!-- # all factors -->
<!-- c <- sdat <- filter(result, Variable=='psiB12') -->

<!-- c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2', 'N1', 'ICC_OV', 'ICC_LV', 'estMean', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'ULSMV', c('estMean', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'WLSMV', c('estMean', 'RB', 'RMSE')]) -->
<!-- colnames(c1) <- c('N2', 'N1','ICC_OV', 'ICC_LV', rep(c('est', 'RB', 'RMSE'), 3)) -->

<!-- kable(c1, format='html', digits=3, row.names = F) %>% -->
<!--   kable_styling(full_width = T) %>% -->
<!--   add_header_above(c(' '=4, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3)) -->
<!--   ## Print out in tex -->
<!-- print(xtable(c1, digits = 3), booktabs = T, include.rownames = F) -->


<!-- ``` -->

<!-- ### Level-2 Item-1 Residual Variance -->

<!-- ```{r} -->

<!-- sdat <- filter(result, Variable=='lambda11') -->

<!-- c <- sdat %>% -->
<!--   group_by(Estimator, N2, N1) %>% -->
<!--   summarise(est = weighted.mean(estMean, wi), -->
<!--             RB = weighted.mean(RB, wi), -->
<!--             RMSE = weighted.mean(RMSE, wi), -->
<!--             Bias = weighted.mean(Bias, wi), -->
<!--             SampVar =weighted.mean(SampVar, wi)) -->

<!-- c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2', 'N1', 'est', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'ULSMV', c('est', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'WLSMV', c('est', 'RB', 'RMSE')]) -->
<!-- colnames(c1) <- c('N2', 'N1', rep(c('est', 'RB', 'RMSE'), 3)) -->

<!-- kable(c1, format='html', digits=3, row.names = F) %>% -->
<!--   kable_styling(full_width = T) %>% -->
<!--   add_header_above(c(' '=2, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3)) -->
<!-- ## Print out in tex -->
<!-- print(xtable(c1, digits = 3), booktabs = T, include.rownames = F) -->


<!-- # all factors -->
<!-- c <- sdat -->

<!-- c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2', 'N1', 'ICC_OV', 'ICC_LV', 'estMean', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'ULSMV', c('estMean', 'RB', 'RMSE')],  -->
<!--            c[ c$Estimator == 'WLSMV', c('estMean', 'RB', 'RMSE')]) -->
<!-- colnames(c1) <- c('N2', 'N1','ICC_OV', 'ICC_LV', rep(c('est', 'RB', 'RMSE'), 3)) -->

<!-- kable(c1, format='html', digits=3, row.names = F) %>% -->
<!--   kable_styling(full_width = T) %>% -->
<!--   add_header_above(c(' '=4, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3)) -->
<!-- ## Print out in tex -->
<!-- print(xtable(c1, digits = 3), booktabs = T, include.rownames = F) -->


<!-- ``` -->