---
title: "ML-CFA: Parameter Bias - Latent Variable ICC"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r init, warning=FALSE, message=FALSE}
rm(list=ls())
source(paste0(getwd(),"/code/load_packages.R"))
#source(paste0(getwd(),"/code/get_data.R"))


```

```{r}
sessionInfo()

# general options
theme_set(theme_bw())
options(digits=3)
```


```{r read-data-in}

# set up vectors of variable names
pvec <- c(paste0('lambda1',1:6), paste0('lambda2',6:10), 'psiW12','psiB1', 'psiB2', 'psiB12', paste0('thetaB',1:10), 'icc_lv1_est', 'icc_lv2_est', paste0('icc_ov',1:10,'_est'))
# stored "true" values of parameters by each condition
ptvec <- c(rep('lambdaT',11), 'psiW12T', 'psiB1T', 'psiB2T', 'psiB12T', rep("thetaBT", 10), rep('icc_lv',2), rep('icc_ov',10))

result <- read_csv(paste0(w.d, "/data/results_bias_est.csv"))

# Set conditions levels as categorical values
result <- result %>%
  mutate(N1 = factor(N1, c("5", "10", "30")),
         N2 = factor(N2, c("30", "50", "100", "200")),
         ICC_OV = factor(ICC_OV, c("0.1","0.3", "0.5")),
         ICC_LV = factor(ICC_LV, c("0.1", "0.5")),
         wi = nRep/500)

```

# Summarizing Results

First, we will plot estimates (botxplots) to show how these estimates changed across conditions.
To summarize the results we will average over the parameters that only differ y indices.
Meaning we will describe the "average factor loading bias" by reporting the average bias for factor loadings.
Additionally, different conditions resultedin different "sample sizes."
By this we mean the number of uses replications.
The different number of cases per condition was accounted for by creating a "weight" variable for each row of the `result` object.
This meant that conditions that had more usable replications counted more towards to averages reported (or count as much as if we averaged over the individual replications).

*[Click here for more details](ml-cfa-parameter-bias-RB.html)


# Latent Variable ICC

```{r}

sdat <- filter(result, Variable %like% 'icc_lv')

sdat <- sdat %>%
  group_by(N1, N2, ICC_OV, ICC_LV, Estimator) %>%
  summarise(estMean = weighted.mean(estMean, wi),
            estSD = weighted.mean(estSD, wi),
            RB = weighted.mean(RB, wi),
            RMSE = weighted.mean(RMSE, wi), 
            Bias = weighted.mean(Bias, wi),
            SampVar = weighted.mean(SampVar, wi))

# first, plot estimates
p1 <- ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  labs(y="Average Latent Variable ICC")

p2 <- ggplot(sdat, aes(y=estSD))+
  geom_boxplot()+
  labs(y="SD of Latent Variable ICC")

p3 <- ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias")

p4 <- ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error")

p5 <- ggplot(sdat, aes(y=Bias))+
  geom_boxplot()+
  labs(y="Sqaured Bias")

p6 <- ggplot(sdat, aes(y=SampVar))+
  geom_boxplot()+
  labs(y="Sampling Variance of Estimates")


p <- (p1 + p2 + p3)/(p4 + p5 + p6) + 
  plot_annotation(title="Summarizing bias indices of LATENT VARIABLE ICC")
p

```

## Single Condition Breakdown

### Estimation Method

```{r}

ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  labs(y="Average Latent Variable ICC",
       title="LATENT VARIABLE ICC by Estimation Method",
       subtitle="Parameter Estimates")+
  facet_wrap(.~Estimator)

ggplot(sdat, aes(y=estSD))+
  geom_boxplot()+
  labs(y="SD of Latent Variable ICC",
       title="LATENT VARIABLE ICC by Estimation Method",
       subtitle="Standard Deviation of Estimates")+
  facet_wrap(.~Estimator)

ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias",
       title="LATENT VARIABLE ICC by Estimation Method",
       subtitle="Relative Bias of Estimates")+
  facet_wrap(.~Estimator)

ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error",
       title="LATENT VARIABLE ICC by Estimation Method",
       subtitle="Root Mean Square Error of Estimates")+
  facet_wrap(.~Estimator)

ggplot(sdat, aes(y=Bias))+
  geom_boxplot()+
  labs(y="Sqaured Bias",
       title="LATENT VARIABLE ICC by Estimation Method",
       subtitle="Squared Bias of Estiamtes")+
  facet_wrap(.~Estimator)

ggplot(sdat, aes(y=SampVar))+
  geom_boxplot()+
  labs(y="Sampling Variance",
       title="LATENT VARIABLE ICC by Estimation Method",
       subtitle="Sampling Variance of Estimates")+
  facet_wrap(.~Estimator)


c <- sdat %>%
  group_by(Estimator) %>%
  summarise(est = mean(estMean),
            RB = mean(RB),
            RMSE = mean(RMSE),
            Bias = mean(Bias),
            SampVar =mean(SampVar))

kable(c, format='html', digits=3,
      caption="Summary Indices of LATENT VARIABLE ICC by Estimation Method") %>%
  kable_styling(full_width = T)

```

### Level-2 Sample Size

```{r}

ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  labs(y="Average Latent Variable ICC",
       title="LATENT VARIABLE ICC by Level-2 Sample Size",
       subtitle="Parameter Estimates")+
  facet_wrap(.~N2)

ggplot(sdat, aes(y=estSD))+
  geom_boxplot()+
  labs(y="SD of Latent Variable ICC",
       title="LATENT VARIABLE ICC by Level-2 Sample Size",
       subtitle="Standard Deviation of Parameter Estimates")+
  facet_wrap(.~N2)

ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias",
       title="LATENT VARIABLE ICC by Level-2 Sample Size",
       subtitle="Relative Bias Parameter Estimates")+
  facet_wrap(.~N2)

ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error",
       title="LATENT VARIABLE ICC by Level-2 Sample Size",
       subtitle="Root Mean Square Error")+
  facet_wrap(.~N2)

ggplot(sdat, aes(y=Bias))+
  geom_boxplot()+
  labs(y="Sqaured Bias",
       title="LATENT VARIABLE ICC by Level-2 Sample Size",
       subtitle="Squared Bias of Parameter Estimates")+
  facet_wrap(.~N2)

ggplot(sdat, aes(y=SampVar))+
  geom_boxplot()+
  labs(y="Sampling Variance of Estimates",
       title="LATENT VARIABLE ICC by Level-2 Sample Size",
       subtitle="Sampling Variance of Parameter Estimates")+
  facet_wrap(.~N2)


c <- sdat %>%
  group_by(N2) %>%
  summarise(est = mean(estMean),
            RB = mean(RB),
            RMSE = mean(RMSE),
            Bias = mean(Bias),
            SampVar =mean(SampVar))

kable(c, format='html', digits=3, 
      caption="Summary Indices of LATENT VARIABLE ICC by Level-2 Sample Size") %>%
  kable_styling(full_width = T)

```

### Level-1 Sample Size

```{r}

ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  labs(y="Average Latent Variable ICC",
       title="LATENT VARIABLE ICC by Level-1",
       subtitle="Parameter Estimates")+
  facet_wrap(.~N1)

ggplot(sdat, aes(y=estSD))+
  geom_boxplot()+
  labs(y="SD of Latent Variable ICC",
       title="LATENT VARIABLE ICC by Level-1 Sample Size",
       subtitle="Standard Deviation of Parameter Estimates")+
  facet_wrap(.~N1)

ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias",
       title="LATENT VARIABLE ICC by Level-1 Sample Size",
       subtitle="Relative Bias of Parameter Estimates")+
  facet_wrap(.~N1)

ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error",
       title="LATENT VARIABLE ICC by Level-1 Sample Size",
       subtitle="Root Mean Square Error")+
  facet_wrap(.~N1)

ggplot(sdat, aes(y=Bias))+
  geom_boxplot()+
  labs(y="Sqaured Bias",
       title="LATENT VARIABLE ICC by Level-1 Sample Size",
       subtitle="Squared Bias of Parameter Estimates")+
  facet_wrap(.~N1)

ggplot(sdat, aes(y=SampVar))+
  geom_boxplot()+
  labs(y="Sampling Variance of Estimates",
       title="LATENT VARIABLE ICC by Level-1 Sample Size",
       subtitle="Sampling Variance of Parameter Estimates")+
  facet_wrap(.~N1)


c <- sdat %>%
  group_by(N1) %>%
  summarise(est = mean(estMean),
            RB = mean(RB),
            RMSE = mean(RMSE),
            Bias = mean(Bias),
            SampVar =mean(SampVar))

kable(c, format='html', digits=3,
      caption="Summary Indices of LATENT VARIABLE ICC  by Level-1 Sample Size") %>%
  kable_styling(full_width = T)

```


### ICC *Observed* Variables

```{r}

ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  labs(y="Average Latent Variable ICC",
       title="LATENT VARIABLE ICC by ICC of Observed Variables",
       subtitle="Parameter Estimates")+
  facet_wrap(.~ICC_OV)

ggplot(sdat, aes(y=estSD))+
  geom_boxplot()+
  labs(y="SD of Latent Variable ICC",
       title="LATENT VARIABLE ICC by ICC of Observed Variables",
       subtitle="Standard Deviation of Parameter Estimates")+
  facet_wrap(.~ICC_OV)

ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias",
       title="LATENT VARIABLE ICC by ICC of Observed Variables",
       subtitle="Relative Bias of Parameter Estimates")+
  facet_wrap(.~ICC_OV)

ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error",
       title="LATENT VARIABLE ICC by ICC of Observed Variables",
       subtitle="Root Mean Square Error of Parameter Estimates")+
  facet_wrap(.~ICC_OV)

ggplot(sdat, aes(y=Bias))+
  geom_boxplot()+
  labs(y="Sqaured Bias",
       title="LATENT VARIABLE ICC by ICC of Observed Variables",
       subtitle="Squared Bias of Parameter Estimates")+
  facet_wrap(.~ICC_OV)

ggplot(sdat, aes(y=SampVar))+
  geom_boxplot()+
  labs(y="Sampling Variance of Estimates",
       title="LATENT VARIABLE ICC by ICC of Observed Variables",
       subtitle="Sampling Variance of Parameter Estimates")+
  facet_wrap(.~ICC_OV)


c <- sdat %>%
  group_by(ICC_OV) %>%
  summarise(est = mean(estMean),
            RB = mean(RB),
            RMSE = mean(RMSE),
            Bias = mean(Bias),
            SampVar =mean(SampVar))

kable(c, format='html', digits=3, caption="Summary Indices of LATENT VARIABLE ICC by ICC of Observed Variables") %>%
  kable_styling(full_width = T)

```

### ICC *Latent* Variables

```{r}

ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  labs(y="Average Latent Variable ICC",
       title="LATENT VARIABLE ICC by ICC of Latent Variables",
       subtitle="Parameter Estimates")+
  facet_wrap(.~ICC_LV)

ggplot(sdat, aes(y=estSD))+
  geom_boxplot()+
  labs(y="SD of Latent Variable ICC",
       title="LATENT VARIABLE ICC by ICC of Latent Variables",
       subtitle="Standard Deviation of Parameter Estimates")+
  facet_wrap(.~ICC_LV)

ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias",
       title="LATENT VARIABLE ICC by ICC of Latent Variables",
       subtitle="Relative Bias of Parameter Estimates")+
  facet_wrap(.~ICC_LV)

ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error",
       title="LATENT VARIABLE ICC by ICC of Latent Variables",
       subtitle="Root Mean Square Error of Parameter Estimates")+
  facet_wrap(.~ICC_LV)

ggplot(sdat, aes(y=Bias))+
  geom_boxplot()+
  labs(y="Sqaured Bias",
       title="LATENT VARIABLE ICC by ICC of Latent Variables",
       subtitle="Squared Bias of Parameter Estimates")+
  facet_wrap(.~ICC_LV)

ggplot(sdat, aes(y=SampVar))+
  geom_boxplot()+
  labs(y="Sampling Variance of Estimates",
       title="LATENT VARIABLE ICC by ICC of Latent Variables",
       subtitle="Sampling Variance of Parameter Estimates")+
  facet_wrap(.~ICC_LV)


c <- sdat %>%
  group_by(ICC_LV) %>%
  summarise(est = mean(estMean),
            RB = mean(RB),
            RMSE = mean(RMSE),
            Bias = mean(Bias),
            SampVar =mean(SampVar))

kable(c, format='html', digits=3,
      caption="Summary Indices of LATENT VARIABLE ICC by ICC of Latent Variables") %>%
  kable_styling(full_width = T)

```

## By Estimation Method and Sample Sizes

### Estimation Method & Level-2 Sample Size

```{r}

ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  labs(y="Average Latent Variable ICC")+
  facet_grid(N2~Estimator)

ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias")+
  facet_grid(N2~Estimator)

ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error")+
  facet_grid(N2~Estimator)

c <- sdat %>%
  group_by(Estimator, N2) %>%
  summarise(est = mean(estMean),
            RB = mean(RB),
            RMSE = mean(RMSE),
            Bias = mean(Bias),
            SampVar =mean(SampVar))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2', 'est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'ULSMV', c('est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'WLSMV', c('est', 'RB', 'RMSE')])
colnames(c1) <- c('N2',  rep(c('est', 'RB', 'RMSE'), 3))

kable(c1, format='html', digits=3, row.names = F) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '=1, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3))

```

### Estimation Method & Level-1 Sample Size

```{r}

ggplot(sdat, aes(y=estMean))+
  geom_boxplot()+
  labs(y="Average Latent Variable ICC")+
  facet_grid(N1~Estimator)

ggplot(sdat, aes(y=RB))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias")+
  facet_grid(N1~Estimator)

ggplot(sdat, aes(y=RMSE))+
  geom_boxplot()+
  labs(y="Root Mean Square Error")+
  facet_grid(N1~Estimator)

c <- sdat %>%
  group_by(Estimator, N1) %>%
  summarise(est = mean(estMean),
            RB = mean(RB),
            RMSE = mean(RMSE),
            Bias = mean(Bias),
            SampVar =mean(SampVar))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N1', 'est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'ULSMV', c('est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'WLSMV', c('est', 'RB', 'RMSE')])
colnames(c1) <- c('N1',  rep(c('est', 'RB', 'RMSE'), 3))

kable(c1, format='html', digits=3, row.names = F) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '=1, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3))
```

### Estimation Method, Level-2 Sample Size & Level-1 Sample Size

```{r}

ggplot(sdat, aes(y=estMean,x=N1, group=N1))+
  geom_boxplot()+
  labs(y="Average Latent Variable ICC")+
  facet_grid(N2~Estimator)

ggplot(sdat, aes(y=RB,x=N1, group=N1))+
  geom_boxplot()+
  geom_hline(yintercept=-10, color="red", linetype="dashed")+
  geom_hline(yintercept=10, color="red", linetype="dashed")+
  labs(y="Relative Bias")+
  facet_grid(N2~Estimator)

ggplot(sdat, aes(y=RMSE,x=N1, group=N1))+
  geom_boxplot()+
  labs(y="Root Mean Square Error")+
  facet_grid(N2~Estimator)

c <- sdat %>%
  group_by(Estimator, N2, N1) %>%
  summarise(est = mean(estMean),
            RB = mean(RB),
            RMSE = mean(RMSE),
            Bias = mean(Bias),
            SampVar =mean(SampVar))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2','N1', 'est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'ULSMV', c('est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'WLSMV', c('est', 'RB', 'RMSE')])
colnames(c1) <- c('N2','N1',  rep(c('est', 'RB', 'RMSE'), 3))

kable(c1, format='html', digits=3, row.names = F) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '=2, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3))

```

## Bias by all Conditions


```{r}

c <- sdat %>%
  group_by(Estimator, N2, N1, ICC_OV, ICC_LV) %>%
  summarise(est = mean(estMean),
            RB = mean(RB),
            RMSE = mean(RMSE),
            Bias = mean(Bias),
            SampVar =mean(SampVar))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2','N1', 'ICC_OV', 'ICC_LV', 'est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'ULSMV', c('est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'WLSMV', c('est', 'RB', 'RMSE')])
colnames(c1) <- c('N2','N1','ICC_OV', 'ICC_LV',  rep(c('est', 'RB', 'RMSE'), 3))

kable(c1, format='html', digits=3, row.names = F) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '=4, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3))

```


## Relative Efficiency by Sample Sizes

```{r}

sdat <- filter(result, Variable %like% 'icc_lv')

c <- sdat %>%
  group_by(Estimator, N2, N1) %>%
  summarise(mu = weighted.mean(muRE, wi),
            mw = weighted.mean(mwRE, wi),
            uw = weighted.mean(uwRE, wi))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2','N1', 'mu', 'mw', 'uw')])
colnames(c1) <- c('N2','N1',c('MLR/ULSMV', 'MLR/WLSMV', 'ULSMV/WLSMV'))

kable(c1, format='html', digits=3, row.names = F) %>%
  kable_styling(full_width = T)


```

## Relative Efficiency by All Conditions

```{r}

c <- sdat %>%
  group_by(Estimator, N2, N1, ICC_OV, ICC_LV) %>%
  summarise(mu = weighted.mean(muRE, wi),
            mw = weighted.mean(mwRE, wi),
            uw = weighted.mean(uwRE, wi))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2','N1','ICC_OV', 'ICC_LV',  'mu', 'mw', 'uw')])
colnames(c1) <- c('N2','N1', 'ICC_OV', 'ICC_LV',c('MLR/ULSMV', 'MLR/WLSMV', 'ULSMV/WLSMV'))

kable(c1, format='html', digits=3, row.names = F) %>%
  kable_styling(full_width = T)


```


# Manuscript Table

```{r man-table}


c <- sdat %>%
  group_by(Estimator, N2, N1) %>%
  summarise(est = weighted.mean(estMean, wi),
            RB = weighted.mean(RB, wi),
            RMSE = weighted.mean(RMSE, wi))

c1 <- cbind(c[ c$Estimator == 'MLR', c( 'N2','N1', 'est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'ULSMV', c('est', 'RB', 'RMSE')], 
           c[ c$Estimator == 'WLSMV', c('est', 'RB', 'RMSE')])
colnames(c1) <- c('N2','N1',  rep(c('est', 'RB', 'RMSE'), 3))

kable(c1, format='html', digits=3, row.names = F) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '=2, 'MLR'=3, 'ULSMV'=3, 'WLSMV'=3))


print(xtable(c1, digits = 3,align=c("l", "l", "l", rep("r",9)),
             display=c("s", "d","d", rep("f",9)),
             caption="Mean Latent Variable ICC, Relative Bias, and RMSE by Estimation Method",
             label="tb:fct"),
      booktabs = T, include.rownames = F,
      caption.placement = "top")

```

