---
title: "Correlation among Parameter Estimates: Level-2 Residual Variances"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r init, warning=FALSE, message=FALSE}
rm(list=ls())
source(paste0(getwd(),"/code/load_packages.R"))
source(paste0(getwd(),"/code/get_data.R"))

# subset to data with admissible replications
sim_results <- filter(sim_results, Converge==1 & Admissible==1)

```

# General Descrition

On this page, we are investigating the correlation among parameter estimates between estimation methods.
We do this by

1. Subsetting the data to the parameter of interest
2. Reshaping the data to wide
3. Compute the correlation
4. Compute the proportion of admissible cases by comparison (i.e., proportion of replications that were used to compute correlation). This gives us an indication of how convergence varied across estimation methods
5. Reshape to long data for plotting
6. Plot correlation estimates in boxplots with points overlayed

# Compute figure pieces

## Factor Loadings 

```{r}

# keep variables
keepVar <- c("Condition", "Replication", "ss_l1", "ss_l2", "icc_ov", "icc_lv", "Estimator", paste0("lambda", c(11:16, 26:29, 210)))

sim_res1 <- sim_results[, keepVar]

sim_res1 <- sim_res1%>%
  pivot_longer(cols = starts_with("lambda"),
               names_to = "lambda",
               values_to = "est") %>%
  pivot_wider(id_cols=c("Condition","Replication", "ss_l1", "ss_l2", "icc_ov", "icc_lv", "lambda"),
              names_from = "Estimator",
              values_from = "est")

cor.est <- sim_res1 %>%
  group_by(ss_l1, ss_l2, icc_ov, icc_lv, lambda) %>%
  summarise(
    r_mlr_ulsmv = cor(MLR, ULSMV,use = "pairwise.complete"),
    cprop_mlr_ulsmv = (1-(sum(is.na(MLR + ULSMV))/500)) ,
    r_mlr_wlsmv = cor(MLR, WLSMV,use = "pairwise.complete"),
    cprop_mlr_wlsmv = (1-(sum(is.na(MLR + WLSMV))/500)),
    r_ulsmv_wlsmv = cor(ULSMV, WLSMV,use = "pairwise.complete"),
    cprop_ulsmv_wlsmv = (1-(sum(is.na(ULSMV + WLSMV))/500))
  )

a1 <- cor.est %>%
  pivot_longer(cols= starts_with("r_"),
               names_to= "Cor",
               values_to = "Est") %>%
  mutate(Cor = substring(Cor, 3))

a2 <- cor.est %>%
  pivot_longer(cols= starts_with("cprop_"),
               names_to= "Cor",
               values_to = "Cprop")%>%
  mutate(Cor = substring(Cor, 7))

cor.est <- left_join(a1[,c(1:5,9:10)], a2[,c(1:5,9:10)]) %>%
  group_by(ss_l1, ss_l2, icc_ov, icc_lv, Cor)%>%
  summarise(Est = mean(Est),
            Cprop = mean(Cprop))


cor.est$Cor <- factor(cor.est$Cor,
                      levels=c("mlr_ulsmv", "mlr_wlsmv", "ulsmv_wlsmv"),
                      labels=c("cor(MLR, ULSMV)",
                               "cor(MLR, WLSMV)",
                               "cor(ULSMV, WLSMV)"),
                      ordered=T)

cor.est$C90 <- as.factor(ifelse(cor.est$Cprop >= 0.9, ">= 90%", "< 90%"))
cor.est$C95 <- as.factor(ifelse(cor.est$Cprop >= 0.95, ">= 95%", "< 95%"))


cols=c("< 90%"="#56B4E9", ">= 90%"="#CC79A7")
shps=c("< 90%"=16, ">= 90%"=17)
p1 <- ggplot(cor.est, aes(x=Cor, y=Est)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(data=filter(cor.est, C90=="< 90%"),
              width=0.3, size=2, alpha=0.7,
              aes(x=Cor, y=Est,
                  color="< 90%", shape="< 90%")) +
  geom_jitter(data=filter(cor.est, C90==">= 90%"),
              width=0.3, size=2, alpha=0.7,
              aes(x=Cor, y=Est,
                  color=">= 90%", shape=">= 90%")) +
  lims(y=c(0,1))+
  labs(y="Correlation",
       x=NULL, tag="A",
       title="Factor Loadings")+
  scale_color_manual(name="% Admissible", values=cols)+
  scale_shape_manual(name="% Admissible", values=shps)+
  theme_bw()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.position = c(0.5,0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=12),
        axis.title.y = element_text(size=12),
        axis.text.y = element_text(size=10),
        axis.text.x = element_text(angle=20, hjust=0.8,
                                   vjust = 0.8, size=11))
p1


```

## Factor Covariance: Level-1

```{r}

# keep variables
keepVar <- c("Condition", "Replication", "ss_l1", "ss_l2", "icc_ov", "icc_lv", "Estimator", "psiW12")

sim_res1 <- sim_results[, keepVar]

sim_res1 <- sim_res1%>%
  pivot_wider(id_cols=c("Condition","Replication", "ss_l1", "ss_l2", "icc_ov", "icc_lv"),
              names_from = "Estimator",
              values_from = "psiW12")

cor.est <- sim_res1 %>%
  group_by(ss_l1, ss_l2, icc_ov, icc_lv) %>%
  summarise(
    r_mlr_ulsmv = cor(MLR, ULSMV,use = "pairwise.complete"),
    cprop_mlr_ulsmv = (1-(sum(is.na(MLR + ULSMV))/500)) ,
    r_mlr_wlsmv = cor(MLR, WLSMV,use = "pairwise.complete"),
    cprop_mlr_wlsmv = (1-(sum(is.na(MLR + WLSMV))/500)),
    r_ulsmv_wlsmv = cor(ULSMV, WLSMV,use = "pairwise.complete"),
    cprop_ulsmv_wlsmv = (1-(sum(is.na(ULSMV + WLSMV))/500))
  )

a1 <- cor.est %>%
  pivot_longer(cols= starts_with("r_"),
               names_to= "Cor",
               values_to = "Est") %>%
  mutate(Cor = substring(Cor, 3))

a2 <- cor.est %>%
  pivot_longer(cols= starts_with("cprop_"),
               names_to= "Cor",
               values_to = "Cprop")%>%
  mutate(Cor = substring(Cor, 7))

cor.est <- left_join(a1[,c(1:4,8:9)], a2[,c(1:4,8:9)])

cor.est$Cor <- factor(cor.est$Cor,
                      levels=c("mlr_ulsmv", "mlr_wlsmv", "ulsmv_wlsmv"),
                      labels=c("cor(MLR, ULSMV)",
                               "cor(MLR, WLSMV)",
                               "cor(ULSMV, WLSMV)"),
                      ordered=T)

cor.est$C90 <- as.factor(ifelse(cor.est$Cprop >= 0.9, ">= 90%", "< 90%"))
cor.est$C95 <- as.factor(ifelse(cor.est$Cprop >= 0.95, ">= 95%", "< 95%"))

cols=c("< 90%"="#56B4E9", ">= 90%"="#CC79A7")
shps=c("< 90%"=16, ">= 90%"=17)
p2 <- ggplot(cor.est, aes(x=Cor, y=Est)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(data=filter(cor.est, C90=="< 90%"),
              width=0.3, size=2, alpha=0.7,
              aes(x=Cor, y=Est,
                  color="< 90%", shape="< 90%")) +
  geom_jitter(data=filter(cor.est, C90==">= 90%"),
              width=0.3, size=2, alpha=0.7,
              aes(x=Cor, y=Est,
                  color=">= 90%", shape=">= 90%")) +
  lims(y=c(0,1))+
  labs(y="Correlation",
       x=NULL, tag="B",
       title="Factor Covariance (Level-1)")+
  scale_color_manual(name="% Admissible", values=cols)+
  scale_shape_manual(name="% Admissible", values=shps)+
  theme_bw()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.position = c(0.5,0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=12),
        axis.title.y = element_text(size=12),
        axis.text.y = element_text(size=10),
        axis.text.x = element_text(angle=20, hjust=0.8,
                                   vjust = 0.8, size=11))
p2

```

## Level-2 Factor Covaraince

```{r}

# keep variables
keepVar <- c("Condition", "Replication", "ss_l1", "ss_l2", "icc_ov", "icc_lv", "Estimator", "psiB12")

sim_res1 <- sim_results[, keepVar]

sim_res1 <- sim_res1%>%
  pivot_wider(id_cols=c("Condition","Replication", "ss_l1", "ss_l2", "icc_ov", "icc_lv"),
              names_from = "Estimator",
              values_from = "psiB12")

cor.est <- sim_res1 %>%
  group_by(ss_l1, ss_l2, icc_ov, icc_lv) %>%
  summarise(
    r_mlr_ulsmv = cor(MLR, ULSMV,use = "pairwise.complete"),
    cprop_mlr_ulsmv = (1-(sum(is.na(MLR + ULSMV))/500)) ,
    r_mlr_wlsmv = cor(MLR, WLSMV,use = "pairwise.complete"),
    cprop_mlr_wlsmv = (1-(sum(is.na(MLR + WLSMV))/500)),
    r_ulsmv_wlsmv = cor(ULSMV, WLSMV,use = "pairwise.complete"),
    cprop_ulsmv_wlsmv = (1-(sum(is.na(ULSMV + WLSMV))/500))
  )

a1 <- cor.est %>%
  pivot_longer(cols= starts_with("r_"),
               names_to= "Cor",
               values_to = "Est") %>%
  mutate(Cor = substring(Cor, 3))

a2 <- cor.est %>%
  pivot_longer(cols= starts_with("cprop_"),
               names_to= "Cor",
               values_to = "Cprop")%>%
  mutate(Cor = substring(Cor, 7))

cor.est <- left_join(a1[,c(1:4,8:9)], a2[,c(1:4,8:9)])

cor.est$Cor <- factor(cor.est$Cor,
                      levels=c("mlr_ulsmv", "mlr_wlsmv", "ulsmv_wlsmv"),
                      labels=c("cor(MLR, ULSMV)",
                               "cor(MLR, WLSMV)",
                               "cor(ULSMV, WLSMV)"),
                      ordered=T)

cor.est$C90 <- as.factor(ifelse(cor.est$Cprop >= 0.9, ">= 90%", "< 90%"))
cor.est$C95 <- as.factor(ifelse(cor.est$Cprop >= 0.95, ">= 95%", "< 95%"))

cols=c("< 90%"="#56B4E9", ">= 90%"="#CC79A7")
shps=c("< 90%"=16, ">= 90%"=17)
p3 <- ggplot(cor.est, aes(x=Cor, y=Est)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(data=filter(cor.est, C90=="< 90%"),
              width=0.3, size=2, alpha=0.7,
              aes(x=Cor, y=Est,
                  color="< 90%", shape="< 90%")) +
  geom_jitter(data=filter(cor.est, C90==">= 90%"),
              width=0.3, size=2, alpha=0.7,
              aes(x=Cor, y=Est,
                  color=">= 90%", shape=">= 90%")) +
  lims(y=c(0,1))+
  labs(y="Correlation",
       x=NULL,tag="C",
       title="Factor Covariance (Level-2)")+
  scale_color_manual(name="% Admissible", values=cols)+
  scale_shape_manual(name="% Admissible", values=shps)+
  theme_bw()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.position = c(0.5,0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=12),
        axis.title.y = element_text(size=12),
        axis.text.y = element_text(size=10),
        axis.text.x = element_text(angle=20, hjust=0.8,
                                   vjust = 0.8, size=11))
p3

```

## Level-2 Factor Variance

```{r}

# keep variables
keepVar <- c("Condition", "Replication", "ss_l1", "ss_l2", "icc_ov", "icc_lv", "Estimator", "psiB1", "psiB2")

sim_res1 <- sim_results[, keepVar]

sim_res1 <- sim_res1%>%
  pivot_longer(cols = starts_with("psiB"),
               names_to = "psiB",
               values_to = "est") %>%
  pivot_wider(id_cols=c("Condition","Replication", "ss_l1", "ss_l2", "icc_ov", "icc_lv", "psiB"),
              names_from = "Estimator",
              values_from = "est")

cor.est <- sim_res1 %>%
  group_by(ss_l1, ss_l2, icc_ov, icc_lv, psiB) %>%
  summarise(
    r_mlr_ulsmv = cor(MLR, ULSMV,use = "pairwise.complete"),
    cprop_mlr_ulsmv = (1-(sum(is.na(MLR + ULSMV))/500)) ,
    r_mlr_wlsmv = cor(MLR, WLSMV,use = "pairwise.complete"),
    cprop_mlr_wlsmv = (1-(sum(is.na(MLR + WLSMV))/500)),
    r_ulsmv_wlsmv = cor(ULSMV, WLSMV,use = "pairwise.complete"),
    cprop_ulsmv_wlsmv = (1-(sum(is.na(ULSMV + WLSMV))/500))
  )

a1 <- cor.est %>%
  pivot_longer(cols= starts_with("r_"),
               names_to= "Cor",
               values_to = "Est") %>%
  mutate(Cor = substring(Cor, 3))

a2 <- cor.est %>%
  pivot_longer(cols= starts_with("cprop_"),
               names_to= "Cor",
               values_to = "Cprop")%>%
  mutate(Cor = substring(Cor, 7))

cor.est <- left_join(a1[,c(1:5,9:10)], a2[,c(1:5,9:10)]) %>%
  group_by(ss_l1, ss_l2, icc_ov, icc_lv, Cor)%>%
  summarise(Est = mean(Est),
            Cprop = mean(Cprop))


cor.est$Cor <- factor(cor.est$Cor,
                      levels=c("mlr_ulsmv", "mlr_wlsmv", "ulsmv_wlsmv"),
                      labels=c("cor(MLR, ULSMV)",
                               "cor(MLR, WLSMV)",
                               "cor(ULSMV, WLSMV)"),
                      ordered=T)

cor.est$C90 <- as.factor(ifelse(cor.est$Cprop >= 0.9, ">= 90%", "< 90%"))
cor.est$C95 <- as.factor(ifelse(cor.est$Cprop >= 0.95, ">= 95%", "< 95%"))

cols=c("< 90%"="#56B4E9", ">= 90%"="#CC79A7")
shps=c("< 90%"=16, ">= 90%"=17)
p4 <- ggplot(cor.est, aes(x=Cor, y=Est)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(data=filter(cor.est, C90=="< 90%"),
              width=0.3, size=2, alpha=0.7,
              aes(x=Cor, y=Est,
                  color="< 90%", shape="< 90%")) +
  geom_jitter(data=filter(cor.est, C90==">= 90%"),
              width=0.3, size=2, alpha=0.7,
              aes(x=Cor, y=Est,
                  color=">= 90%", shape=">= 90%")) +
  lims(y=c(0,1))+
  labs(y="Correlation",
       x=NULL,tag="D",
       title="Factor Variances (Level-2)")+
  scale_color_manual(name="% Admissible", values=cols)+
  scale_shape_manual(name="% Admissible", values=shps)+
  theme_bw()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.position = c(0.5,0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=12),
        axis.title.y = element_text(size=12),
        axis.text.y = element_text(size=10),
        axis.text.x = element_text(angle=20, hjust=0.8,
                                   vjust = 0.8, size=11))
p4

```

## Level-2 Residual Variances

```{r}

# keep variables
keepVar <- c("Condition", "Replication", "ss_l1", "ss_l2", "icc_ov", "icc_lv", "Estimator", paste0("thetaB",1:10))

sim_res1 <- sim_results[, keepVar]

sim_res1 <- sim_res1%>%
  pivot_longer(cols = starts_with("thetaB"),
               names_to = "theta",
               values_to = "est") %>%
  pivot_wider(id_cols=c("Condition","Replication", "ss_l1", "ss_l2", "icc_ov", "icc_lv", "theta"),
              names_from = "Estimator",
              values_from = "est")

cor.est <- sim_res1 %>%
  group_by(ss_l1, ss_l2, icc_ov, icc_lv, theta) %>%
  summarise(
    r_mlr_ulsmv = cor(MLR, ULSMV,use = "pairwise.complete"),
    cprop_mlr_ulsmv = (1-(sum(is.na(MLR + ULSMV))/500)) ,
    r_mlr_wlsmv = cor(MLR, WLSMV,use = "pairwise.complete"),
    cprop_mlr_wlsmv = (1-(sum(is.na(MLR + WLSMV))/500)),
    r_ulsmv_wlsmv = cor(ULSMV, WLSMV,use = "pairwise.complete"),
    cprop_ulsmv_wlsmv = (1-(sum(is.na(ULSMV + WLSMV))/500))
  )

a1 <- cor.est %>%
  pivot_longer(cols= starts_with("r_"),
               names_to= "Cor",
               values_to = "Est") %>%
  mutate(Cor = substring(Cor, 3))

a2 <- cor.est %>%
  pivot_longer(cols= starts_with("cprop_"),
               names_to= "Cor",
               values_to = "Cprop")%>%
  mutate(Cor = substring(Cor, 7))

cor.est <- left_join(a1[,c(1:5,9:10)], a2[,c(1:5,9:10)]) %>%
  group_by(ss_l1, ss_l2, icc_ov, icc_lv, Cor)%>%
  summarise(Est = mean(Est),
            Cprop = mean(Cprop))


cor.est$Cor <- factor(cor.est$Cor,
                      levels=c("mlr_ulsmv", "mlr_wlsmv", "ulsmv_wlsmv"),
                      labels=c("cor(MLR, ULSMV)",
                               "cor(MLR, WLSMV)",
                               "cor(ULSMV, WLSMV)"),
                      ordered=T)

cor.est$C90 <- as.factor(ifelse(cor.est$Cprop >= 0.9, ">= 90%", "< 90%"))
cor.est$C95 <- as.factor(ifelse(cor.est$Cprop >= 0.95, ">= 95%", "< 95%"))

cols=c("< 90%"="#56B4E9", ">= 90%"="#CC79A7")
shps=c("< 90%"=16, ">= 90%"=17)
p5 <- ggplot(cor.est, aes(x=Cor, y=Est)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(data=filter(cor.est, C90=="< 90%"),
              width=0.3, size=2, alpha=0.7,
              aes(x=Cor, y=Est,
                  color="< 90%", shape="< 90%")) +
  geom_jitter(data=filter(cor.est, C90==">= 90%"),
              width=0.3, size=2, alpha=0.7,
              aes(x=Cor, y=Est,
                  color=">= 90%", shape=">= 90%")) +
  lims(y=c(0,1))+
  labs(y="Correlation",
       x=NULL, tag="E",
       title="Residual Variance (Level-2)")+
  scale_color_manual(name="% Admissible", values=cols)+
  scale_shape_manual(name="% Admissible", values=shps)+
  theme_bw()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.position = c(0.5,0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=12),
        axis.title.y = element_text(size=12),
        axis.text.y = element_text(size=10),
        axis.text.x = element_text(angle=20, hjust=0.8,
                                   vjust = 0.8, size=11))
p5

```


# Publication Figure

Merge the pieces back together.

```{r}

p1 <- p1 + theme(legend.position = c(0.5,0.5))
leg <- cowplot::get_legend(p1)
p1 <- p1 + theme(legend.position = "none")
p2 <- p2 + theme(legend.position = "none")
p3 <- p3 + theme(legend.position = "none")
p4 <- p4 + theme(legend.position = "none")
p5 <- p5 + theme(legend.position = "none")

p <- p1 + p2 + p3 + p4 + p5 + leg
p

ggsave("fig/estimate_correlation_pub.pdf",p, units="in", height=6, width=10)

```

```{r session-info}
sessionInfo()
```

