---
title: "Design Effects on Relative Bias of Parameter Estimates"
date: "2020-06-01"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

The purpose of this page is to identify the impact of design factors on standard error estimates.
This is done using analysis of variance (factorial) on the estimates of relative bias (RB) for the estimated parameter.

# Packages and Set-Up


```{r init, warning=FALSE, message=FALSE}

rm(list=ls())
source(paste0(getwd(),"/code/load_packages.R"))
source(paste0(getwd(),"/code/get_data.R"))
source(paste0(getwd(),"/code/r_functions.R"))

# general options
theme_set(theme_bw())
options(digits=3)

##Chunk iptions
knitr::opts_chunk$set(out.width="225%")

```


# Data Management

```{r data, tidy=T}

# set up vectors of variable names
pvec <- c(paste0('lambda1',1:6), paste0('lambda2',6:10), 'psiW12','psiB1', 'psiB2', 'psiB12', paste0('thetaB',1:10), 'icc_lv1_est', 'icc_lv2_est', paste0('icc_ov',1:10,'_est'))
# stored "true" values of parameters by each condition
ptvec <- c(rep('lambdaT',11), 'psiW12T', 'psiB1T', 'psiB2T', 'psiB12T', rep("thetaBT", 10), rep('icc_lv',2), rep('icc_ov',10))


# take out non-converged/inadmissible cases
sim_results <- filter(sim_results, Converge==1, Admissible==1)

# Set conditions levels as categorical values
sim_results <- sim_results %>%
  mutate(N1 = factor(N1, c("5", "10", "30")),
         N2 = factor(N2, c("30", "50", "100", "200")),
         ICC_OV = factor(ICC_OV, c("0.1","0.3", "0.5")),
         ICC_LV = factor(ICC_LV, c("0.1", "0.5")))

# convert to long format
long_res1 <- sim_results[,c("Condition", "Replication", "N1", "N2", "ICC_OV", "ICC_LV", "Estimator", pvec)] %>%
  pivot_longer(
    cols = all_of(pvec),
    names_to = "Parameter",
    values_to = "Estimate"
  )

long_res2 <- tibble(sim_results[,c("Condition", "Replication", "N1", "N2", "ICC_OV", "ICC_LV", "Estimator", ptvec)], .name_repair="universal")
ptvec <- colnames(long_res2)[8:44]
long_res2 <- long_res2 %>%
  pivot_longer(
    cols = all_of(ptvec),
    names_to = "ParameterT",
    values_to = "Truth"
  )

long_results <- long_res1
long_results$ParameterT <- long_res2$ParameterT
long_results$Truth <- long_res2$Truth

```

Now, we are only going to do ANOVA on the relative bias estimates (RB).


```{r}

long_results <- long_results %>%
  mutate(RB = ((Estimate - Truth))/Truth*100)


# Object to Story Results
resultsList <- list()


```


# ANOVA and effect sizes for distributional differences

For this simulation experiment, there were 5 factors systematically varied.
Of these 5 factors, 4 were factors influencing the observed data and 1 were factors pertaining to estimation and model fitting.
The factors were

  1. Level-1 sample size (5, 10, 30)
  2. Level-2 sample size (30, 50, 100, 200)
  3. Observed indicator ICC (.1, .3, .5)
  4. Latent variable ICC (.1, .5)
  5. Model estimator (MLR, ULSMV, WLSMV)
  
For each parameter, an analysis of variance (ANOVA) was conducted in order to test how much influence each of these design factors.

General Linear Model investigated for estimated parameter was: 
\[
Y_{ijklmn} = \mu + \alpha_{j} + \beta_{k} + \gamma_{l} + \delta_m + \theta_n +\\
(\alpha\beta)_{jk} + (\alpha\gamma)_{jl}+ (\alpha\delta)_{jm}  + (\alpha\theta)_{jn}+ \\
(\beta\gamma)_{kl}+ (\beta\delta)_{km} +  (\beta\theta)_{kn}+ (\gamma\delta)_{lm} + + (\gamma\theta)_{ln} + (\delta\theta)_{mn} + \varepsilon_{ijklmn}
\]
where 

  1. $\mu$ is the grand mean,
  2. $\alpha_{j}$ is the effect of Level-1 sample size,  
  3. $\beta_{k}$ is the effect of Level-2 sample size, 
  4. $\gamma_{l}$ is the effect of Observed indicator ICC, 
  5. $\delta_m$ is the effect of Latent variable ICC, 
  6. $\theta_n$ is the effect of Model estimator , 
  7. $(\alpha\beta)_{jk}$ is the interaction between  Level-1 sample size and Level-2 sample size,
  8. $(\alpha\gamma)_{jl}$ is the interaction between Level-1 sample size and Observed indicator ICC,
  9. $(\alpha\delta)_{jm}$ is the interaction between  Level-1 sample size and Latent variable ICC,
  10. $(\alpha\theta)_{jn}$ is the interaction between  Level-1 sample size and Model estimator ,
  11. $(\beta\gamma)_{kl}$ is the interaction between  Level-2 sample size and Observed indicator ICC,
  12. $(\beta\delta)_{km}$ is the interaction between  Level-2 sample size and Latent variable ICC,
  13. $(\beta\theta)_{kn}$ is the interaction between  Level-2 sample size and Model estimator ,
  14. $(\gamma\delta)_{lm}$ is the interaction between Observed indicator ICC and Latent variable ICC,
  15. $(\gamma\theta)_{ln}$ is the interaction between  Observed indicator ICC and Model estimator ,
  16. $(\delta\theta)_{mn}$ is the interaction between  Latent variable ICC and Model estimator , and
  17. $\varepsilon_{ijklmn}$ is the residual error for the $i^{th}$ observed SE estimate.
  
  
Note that for most of these terms there are actually 2 or 3 terms actually estimated.
These additional terms are because of the categorical nature of each effect so we have to create "reference" groups and calculate the effect of being in a group other than the reference group. 
Higher order interactions were omitted for clarity of interpretation of the model.
If interested in higher-order interactions, please see Maxwell and Delaney (2004).

The real reason the higher order interaction was omitted:
Because I have no clue how to interpret a 5-way interaction (whatever the heck that is), I am limiting the ANOVA to all bivariate interactions.


Diagnostics for factorial ANOVA:

1. Independence of Observations
2. Normality of residuals across cells for the design
3. Homogeneity of variance across cells

Independence of observations is by design, where these data were randomly generated from a known population and observations are across replications and are independent.
The normality assumptions is that the residuals of the models are normally distributed across the design cells. 
The normality assumption is tested by investigation by Shapiro-Wilks Test, the K-S test, and visual inspection of  QQ-plots and histograms. 
The equality of variance is checked through Levene's test across all the different conditions/groupings. 
Furthermore, the plots of the residuals are also indicative of the equality of variance across groups as there should be no apparent pattern to the residual plots. 

## Factor Loadings

### Assumption Checking

```{r ac-anova-fl}

sdat <- filter(long_results, Parameter %like% "lambda")

sdat <- sdat %>%
  group_by(Replication, N1, N2, ICC_OV, ICC_LV, Estimator) %>%
  summarise(RB = mean(RB))

# first, look at summary of RB Estimates
boxplot(sdat$RB)

## model factors...
flist <- c('N1', 'N2', 'ICC_OV', 'ICC_LV', 'Estimator')
## Check assumptions
anova_assumptions_check(
  sdat, 'RB', factors = flist,
  model = as.formula('RB ~ N1 + N2 + ICC_OV + ICC_LV + Estimator + N1:N2 + N1:ICC_OV + N1:ICC_LV + N1:Estimator + N2:ICC_OV + N2:ICC_LV + N2:Estimator + ICC_OV:ICC_LV +  ICC_OV:Estimator  + ICC_LV:Estimator'))

# was bad... Remove extreme outliers
quantile(sdat$RB, c(0.001, 0.01, 0.99, 0.999))

# remove RB>100
sdat <- filter(sdat, RB <= 100)
boxplot(sdat$RB)

# rerun
## Check assumptions
anova_assumptions_check(
  sdat, 'RB', factors = flist,
  model = as.formula('RB ~ N1 + N2 + ICC_OV + ICC_LV + Estimator + N1:N2 + N1:ICC_OV + N1:ICC_LV + N1:Estimator + N2:ICC_OV + N2:ICC_LV + N2:Estimator + ICC_OV:ICC_LV +  ICC_OV:Estimator  + ICC_LV:Estimator'))

```

### ANOVA Results

```{r anova-fl}

model = as.formula('RB ~ N1 + N2 + ICC_OV + ICC_LV + Estimator + N1:N2 + N1:ICC_OV + N1:ICC_LV + N1:Estimator + N2:ICC_OV + N2:ICC_LV + N2:Estimator + ICC_OV:ICC_LV +  ICC_OV:Estimator  + ICC_LV:Estimator')

fit <- aov(model, data = sdat)
fit.out <- summary(fit)
fit.out
resultsList[["FactorLoadings"]] <- cbind(omega2(fit.out), p_omega2(fit.out))
resultsList[["FactorLoadings"]]

```


## Level-1 factor Covariance

### Assumption Checking

```{r ac-anova-l1cv}

sdat <- filter(long_results, Parameter %like% "psiW")

sdat <- sdat %>%
  group_by(Replication, N1, N2, ICC_OV, ICC_LV, Estimator) %>%
  summarise(RB = mean(RB))

# first, look at summary of RB Estimates
boxplot(sdat$RB)

## model factors...
flist <- c('N1', 'N2', 'ICC_OV', 'ICC_LV', 'Estimator')
## Check assumptions
anova_assumptions_check(
  sdat, 'RB', factors = flist,
  model = as.formula('RB ~ N1 + N2 + ICC_OV + ICC_LV + Estimator + N1:N2 + N1:ICC_OV + N1:ICC_LV + N1:Estimator + N2:ICC_OV + N2:ICC_LV + N2:Estimator + ICC_OV:ICC_LV +  ICC_OV:Estimator  + ICC_LV:Estimator'))

# was bad... Remove extreme outliers
quantile(sdat$RB, c(0.001, 0.01, 0.99, 0.999))

# remove RB>100
sdat <- filter(sdat, RB <= 100)
boxplot(sdat$RB)

# rerun
## Check assumptions
anova_assumptions_check(
  sdat, 'RB', factors = flist,
  model = as.formula('RB ~ N1 + N2 + ICC_OV + ICC_LV + Estimator + N1:N2 + N1:ICC_OV + N1:ICC_LV + N1:Estimator + N2:ICC_OV + N2:ICC_LV + N2:Estimator + ICC_OV:ICC_LV +  ICC_OV:Estimator  + ICC_LV:Estimator'))

```

### ANOVA Results

```{r anova-l1cv}

model = as.formula('RB ~ N1 + N2 + ICC_OV + ICC_LV + Estimator + N1:N2 + N1:ICC_OV + N1:ICC_LV + N1:Estimator + N2:ICC_OV + N2:ICC_LV + N2:Estimator + ICC_OV:ICC_LV +  ICC_OV:Estimator  + ICC_LV:Estimator')

fit <- aov(model, data = sdat)
fit.out <- summary(fit)
fit.out
resultsList[["Level1-FactorCovariance"]] <- cbind(omega2(fit.out), p_omega2(fit.out))
resultsList[["Level1-FactorCovariance"]]

```

##  Level-2 factor (co)variances

### Assumption Checking

```{r ac-anova-l2cv}

sdat <- filter(long_results, Parameter %like% "psiB")

sdat <- sdat %>%
  group_by(Replication, N1, N2, ICC_OV, ICC_LV, Estimator) %>%
  summarise(RB = mean(RB))

# first, look at summary of RB Estimates
boxplot(sdat$RB)

## model factors...
flist <- c('N1', 'N2', 'ICC_OV', 'ICC_LV', 'Estimator')
## Check assumptions
anova_assumptions_check(
  sdat, 'RB', factors = flist,
  model = as.formula('RB ~ N1 + N2 + ICC_OV + ICC_LV + Estimator + N1:N2 + N1:ICC_OV + N1:ICC_LV + N1:Estimator + N2:ICC_OV + N2:ICC_LV + N2:Estimator + ICC_OV:ICC_LV +  ICC_OV:Estimator  + ICC_LV:Estimator'))

# was bad... Remove extreme outliers
quantile(sdat$RB, c(0.001, 0.01, 0.99, 0.999))

# remove RB>100
sdat <- filter(sdat, RB <= 100)
boxplot(sdat$RB)

# rerun
## Check assumptions
anova_assumptions_check(
  sdat, 'RB', factors = flist,
  model = as.formula('RB ~ N1 + N2 + ICC_OV + ICC_LV + Estimator + N1:N2 + N1:ICC_OV + N1:ICC_LV + N1:Estimator + N2:ICC_OV + N2:ICC_LV + N2:Estimator + ICC_OV:ICC_LV +  ICC_OV:Estimator  + ICC_LV:Estimator'))

```

### ANOVA Results

```{r anova-l2cv}

model = as.formula('RB ~ N1 + N2 + ICC_OV + ICC_LV + Estimator + N1:N2 + N1:ICC_OV + N1:ICC_LV + N1:Estimator + N2:ICC_OV + N2:ICC_LV + N2:Estimator + ICC_OV:ICC_LV +  ICC_OV:Estimator  + ICC_LV:Estimator')

fit <- aov(model, data = sdat)
fit.out <- summary(fit)
fit.out
resultsList[["Level2-FactorCovariance"]] <- cbind(omega2(fit.out), p_omega2(fit.out))
resultsList[["Level2-FactorCovariance"]]

```


## Level-2 item residual variances

### Assumption Checking

```{r ac-anova-l2r}

sdat <- filter(long_results, Parameter %like% "thetaB")

sdat <- sdat %>%
  group_by(Replication, N1, N2, ICC_OV, ICC_LV, Estimator) %>%
  summarise(RB = mean(RB))

# first, look at summary of RB Estimates
boxplot(sdat$RB)

## model factors...
flist <- c('N1', 'N2', 'ICC_OV', 'ICC_LV', 'Estimator')
## Check assumptions
anova_assumptions_check(
  sdat, 'RB', factors = flist,
  model = as.formula('RB ~ N1 + N2 + ICC_OV + ICC_LV + Estimator + N1:N2 + N1:ICC_OV + N1:ICC_LV + N1:Estimator + N2:ICC_OV + N2:ICC_LV + N2:Estimator + ICC_OV:ICC_LV +  ICC_OV:Estimator  + ICC_LV:Estimator'))

# was bad... Remove extreme outliers
quantile(sdat$RB, c(0.001, 0.01, 0.99, 0.999))

# remove RB>100
sdat <- filter(sdat, RB <= 100)
boxplot(sdat$RB)

# rerun
## Check assumptions
anova_assumptions_check(
  sdat, 'RB', factors = flist,
  model = as.formula('RB ~ N1 + N2 + ICC_OV + ICC_LV + Estimator + N1:N2 + N1:ICC_OV + N1:ICC_LV + N1:Estimator + N2:ICC_OV + N2:ICC_LV + N2:Estimator + ICC_OV:ICC_LV +  ICC_OV:Estimator  + ICC_LV:Estimator'))

```

### ANOVA Results

```{r anova-l2r}

model = as.formula('RB ~ N1 + N2 + ICC_OV + ICC_LV + Estimator + N1:N2 + N1:ICC_OV + N1:ICC_LV + N1:Estimator + N2:ICC_OV + N2:ICC_LV + N2:Estimator + ICC_OV:ICC_LV +  ICC_OV:Estimator  + ICC_LV:Estimator')

fit <- aov(model, data = sdat)
fit.out <- summary(fit)
fit.out
resultsList[["Level2-ResidualCovariance"]] <- cbind(omega2(fit.out), p_omega2(fit.out))
resultsList[["Level2-ResidualCovariance"]]

```





# Summary Table of Effect Sizes

```{r sum-tab-eff}

tb <- cbind(resultsList[[1]], resultsList[[2]], resultsList[[3]], resultsList[[4]])

kable(tb, format='html') %>%
    kable_styling(full_width = T) %>%
    add_header_above(c('Effect'=1,'Factor Loadings'=2,'Level-1 Factor Covariance'=2,'Level-2 Factor (co)variance'=2,'Level-2 Item Residual Variance'=2))

## Print out in tex
#print(xtable(tb, digits = 3), booktabs = T, include.rownames = T)


## Table of partial-omega2
tb <- cbind(resultsList[[1]][,2, drop=F], resultsList[[2]][,2, drop=F], resultsList[[3]][,2, drop=F], resultsList[[4]][,2, drop=F])

kable(tb, format='html') %>%
    kable_styling(full_width = T) %>%
    add_header_above(c('Effect'=1,'Factor Loadings'=2,'Level-1 Factor Covariance'=2,'Level-2 Factor (co)variance'=2,'Level-2 Item Residual Variance'=2))

## Print out in tex
print(xtable(tb, digits = 3), booktabs = T, include.rownames = T)
# 
# 
# ## Table of omega-2
# tb <- cbind(resultsList[[1]][,1, drop=F], resultsList[[2]][,1, drop=F], resultsList[[3]][,1, drop=F], resultsList[[4]][,1, drop=F])
# 
# kable(tb, format='html') %>%
#     kable_styling(full_width = T) %>%
#     add_header_above(c('Effect'=1,'Factor Loadings'=2,'Level-1 Factor Covariance'=2,'Level-2 Factor (co)variance'=2,'Level-2 Item Residual Variance'=2))
# 
# ## Print out in tex
# print(xtable(tb, digits = 3), booktabs = T, include.rownames = T)

```

